### 2021-08-02 article.tex
Initial SPIE template

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}

\title{SPIE journal papers: sample manuscript showing style and formatting specifications}

\author[a]{First Author}
\author[a]{Second Author}
\author[b]{Third Author}
\author[a,b,*]{Fourth Author}
\affil[a]{University Name, Faculty Group, Department, Street Address, City, Country, Postal Code}
\affil[b]{Company Name, Street Address, City, Country, Postal Code}

\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document} 
\maketitle

\begin{abstract}
This document shows the required format and appearance of a manuscript prepared for SPIE journals. It is prepared using LaTeX2e with the class file \texttt{spieman.cls}. Please note that the following journals require the use of structured abstracts in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of Medical Imaging}. Structured abstracts are encouraged for the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}. Guidelines are available on the journal website. Whether structured or single-paragraph, the abstract should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting and indexing databases, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. A list of up to six keywords should immediately follow. 
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

% Include email contact information for corresponding author
{\noindent \footnotesize\textbf{*}Fourth author name,  \linkable{myemail@university.edu} }

\begin{spacing}{2}   % use double spacing for rest of manuscript

\section{Introduction}
\label{sect:intro}  % \label{} allows reference to this section
This document shows the format and appearance of a manuscript prepared for submission to an SPIE journal. Note that this template is only intended to be used as a guideline for author convenience. It is designed for optimum clarity and ease of reading for editors and reviewers, but the template does not reflect the final page layout of a published journal paper. Accepted papers are professionally typeset in XML according to the layout and design of the journal.

\subsection{Use of This Document}

This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.  The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it. Authors may use it as a template to create their own manuscript. While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.

\subsection{English}

Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example. In addition, good English usage is essential. Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced. Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{https://www.editage.com/spie/}. SPIE authors will receive a 15\% discount off their services. A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission. Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.

\subsection{Page Setup and Fonts}

All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.

The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}. If this font is not available, use a similar serif font. The manuscript should not contain headers or footers. Pages should be numbered.

\begin{table}[ht]
\caption{Fonts sizes and styles.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
\hline\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
\hline 
\end{tabular}
\end{center}
\end{table}

\section{Parts of Manuscript}

This section describes the normal structure of a manuscript and how each part should be handled. The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.

\subsection{Title and Author Information}
\label{sect:title}
The article title appears left justified at the top of the first page. The title font is 16 pt., bold. The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized. Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.). The word ``novel'' should not appear in the title, as publication will imply novelty. Avoid the use of acronyms in the title, unless they are widely understood. Appendix A contains more about acronyms.

The list of authors immediately follows the title, 18 points below. The font is 12 pt., bold and the author names are left justified. The author affiliations and addresses follow the names, in 10-pt., normal font and left justified. For multiple affiliations, each affiliation should appear on a separate line. Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations. The corresponding author should be identified with an asterisk, and that person's email address should be provided below the keywords.

\subsection{Abstract}
The abstract should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting journals, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. Please note that the following journals require the use of structured abstracts in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the\textit{ Journal of Medical Imaging}. Structured abstracts are encouraged for the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}. Helpful guidelines for structured abstracts are available on the website of the journal.

\subsection{Subject terms/Keywords}
Keywords are required. Please provide 3-6 keywords related to your paper.

\subsection{Body of Paper}
The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.

To provide transition elements in your paper, it is important to refer back (or forward) to specific sections. Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed...'' or ``Section 2.1 contained a description...'' If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out. When occurring in the middle of a sentence, these words are abbreviated Sec., Ref., Eq., and Fig.

At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).

\subsection{Footnotes}
Textual footnotes should be used rarely to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should generally be avoided. If absolutely necessary, the footnote mark must come at the end of a sentence. To insert a footnote, use the {\verb|\footnote{}|} command.

\subsection{Appendices}
Brief appendices may be included when necessary, such as derivations of equations, proofs of theorems, and details of algorithms. Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.

\subsection{Disclosures}
Conflicts of interest should be declared under a separate header, above Acknowledgments. If the authors have no competing interests to declare, then a statement should be included declaring no conflicts of interest. For assistance generating a disclosure statement, see the form available from  the International Committee of Medical Journal Editors website: \linkable{http://www.icmje.org/conflicts-of-interest/}

\subsection{Acknowledgments}
Acknowledgments and funding information should be added after the conclusion, and before references. Include grant numbers and the full name of the funding body. The acknowledgments section does not have a section number.

\subsection{Data, Materials, and Code Availability}
Availability of data, materials, and/or code used in the research results reported in the manuscript may be declared under the heading "Data, Materials, and Code Availability," following the Acknowledgments section. As relevant, provide specific access information or restrictions for data, materials, and computer code (i.e., links to repository access addresses with guidance on commercial or public access).

\subsection{References}
The References section lists books, articles, and reports that are cited in the paper. This section does not have a section number. The references are numbered in the order in which they are cited. Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.  Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

The references are numbered in the order of their first citation. Citations to the references are made using superscripts, as demonstrated in the preceding paragraph. One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ...''  Two or more references should be separated by a comma with no space between them. Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.

\subsubsection{Reference linking and DOIs}
A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet. The use of DOIs allows readers to easily access cited articles. Authors should include the DOI at the end of each reference in brackets if a DOI is available. See examples at the end of this manuscript. A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}. The inclusion of DOIs will facilitate reference linking and is highly recommended.

In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note'' in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}. The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.

\subsection{Biographies}
A brief professional biography of approximately 75 words may be provided for each author, if available. Biographies should be placed at the end of the paper, after the references. Personal information such as hobbies or birthplace/birthdate should not be included. Author photographs are not published.

\section{Section Formatting}
\label{sect:sections}
In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections. Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references. (Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.

Main section headings are in 12-pt. bold font, left-justified and in title case, where important words are capitalized.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style. The same goes for leading paragraphs of subsections and sub-subsections. Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation. There is no additional space between paragraphs. In LaTeX, paragraphs are separated by blank lines in the source file. Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

\subsection{Subsection Headings}
All important words in a subsection (level 1) header are capitalized. Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end. The heading is left justified and its font is 12 pt. italic.

\subsubsection{Sub-subsection headings}
The first word of a sub-subsection is capitalized. The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known). The heading is left justified and its font is 11 pt. italic.

\section{Figures and Tables}

\subsection{Figures}

Figures are numbered in the order in which they are called out in the text. They should appear in the document in numerical order and as close as possible to their first reference in the text. It may be necessary to move figures or tables around to enhance readability. LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.

Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered. Figure captions are centered below the figure or graph. Figure captions start with the abbreviation ``Fig'' in front of the figure number, followed by a period, and the text in 10-pt. font. See Fig.~\ref{fig:example} for an example.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{mcr3b.eps}
\end{tabular}
\end{center}
\caption 
{ \label{fig:example}
Example of a figure caption. } 
\end{figure}

Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.  In no case, should the article's text be wrapped around a figure. Figure~\ref{fig:example2} shows two side-by-side images. When a figure contains more than one image, the author must submit them as a single image file. Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
\\
(a) \hspace{5.1cm} (b)
\end{tabular}
\end{center}
\caption 
{ \label{fig:example2}
Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
\end{figure}

\subsection{Tables}
Tables are numbered in the order in which they are referenced. They should appear in the document in numerical order and as close as possible to their first reference in the text. It is preferable to have tables appear at the top or bottom of the page, if possible. Table captions are handled identically to those for figures, except that they appear above the table. See Table~\ref{tab:fonts} for an example.

\subsection{Multimedia}
Acceptable file formats, including MOV (.mov), MPEG (.mpg), and MP4 (.mp4), are playable using standard media players, such as VLC or Windows Media Player. The recommended maximum size for each multimedia file is 10-12 MB. Authors must insert a representative still image from the video file in the manuscript as a figure. The caption label will be linked by the publisher to the actual video file. The video may also be mentioned in an existing figure caption. Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.  The video number, file type, and file size should be included in parentheses at the end of the figure caption. See Figure \ref{vid:satellite} for an example.

\begin{video}
\begin{center}
{\includegraphics[height=5cm]{satellite.eps}}
\\
\end{center}
\caption{\label{vid:satellite}This satellite is a still image from Video 1 (Video 1, MPEG, 2.5 MB).}
\end{video}

\appendix    % this command starts appendixes

\section{Miscellaneous Formatting Details}
\label{sect:misc}
At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.

\subsection{Formatting Equations}
Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the field of view is
\begin{equation}
\label{eq:fov}
2 a = \frac{(b + 1)}{3c} \, ,
\end{equation}
where $a$ is the ...''  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma appears after the equation because the next line is a subordinate clause. If the equation ends the sentence, a period should follow the equation. The line following an equation should not be indented unless it is meant to start a new paragraph. Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ...'' or ``Combining Eqs.~(2) and (3), we obtain...'' Note that the word ``Equation'' is spelled out if it begins a sentence, but is abbreviated as ``Eq.'' otherwise. Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq.'' and the following equation number..

\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.  The text of the theorem continues on the same line in normal, 10-pt. font, achieved in LaTeX using \verb|\footnotesize|.  For example,

\vspace{2ex}\noindent{\footnotesize\textbf{Theorem 1.} For any unbiased estimator...}

% \disclosures 
\subsection*{Disclosures}
Conflicts of interest should be declared under a separate header. If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.

\subsection* {Acknowledgments}
This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

\subsection* {Data, Materials, and Code Availability} 
As relevant, the availability of data, materials, and/or software code used in the research results reported in the manuscript may be declared in this section. (Note: this section is required for the \textit{Journal of Biomedical Optics} and \textit{Neurophotonics}.) Provide specific access information or restrictions for data, materials, and computer code (i.e., links to repository access addresses with guidance on commercial or public access).

%%%%% References %%%%%

\bibliography{report}   % bibliography data in report.bib
\bibliographystyle{spiejour}   % makes bibtex use spiejour.bst

%%%%% Biographies of authors %%%%%

\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering. He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.  He is the author of more than 50 journal papers and has written three book chapters. His current research interests include optical interconnects, holography, and optoelectronic systems. He is a member of SPIE.

\vspace{1ex}
\noindent Biographies and photographs of the other authors are not available.

\listoffigures
\listoftables

\end{spacing}
\end{document}

### 2021-08-31 article.tex
Remove template content

@@
-\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
-%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
+\documentclass[12pt]{spieman}
+
 \usepackage{amsmath,amsfonts,amssymb}
@@
 
+% ---------------------------------------------------------------------------------------
+% BEGIN TITLE AND AUTHORS
+% ---------------------------------------------------------------------------------------
+
 \title{SPIE journal papers: sample manuscript showing style and formatting specifications}
 
-\author[a]{First Author}
-\author[a]{Second Author}
-\author[b]{Third Author}
-\author[a,b,*]{Fourth Author}
-\affil[a]{University Name, Faculty Group, Department, Street Address, City, Country, Postal Code}
-\affil[b]{Company Name, Street Address, City, Country, Postal Code}
+\author[a]{Colin T. Sullender}
+\author[a]{Adam Santorelli}
+\author[a]{Christopher Smith}
+\author[a]{Lisa M. Richards}
+\author[a,*]{Andrew K. Dunn}
+\affil[a]{The University of Texas at Austin, Department of Biomedical Engineering, 107 W. Dean Keeton St. Stop C0800, Austin, TX, 78712, USA}
 
+% ----------------------------------------------------------------------------------------
+% BEGIN DOCUMENT
+% ----------------------------------------------------------------------------------------
 \renewcommand{\cftdotsep}{\cftnodots}
@@
 
+% ----------------------------------------------------------------------------------------
+% BEGIN ABSTRACT
+% ----------------------------------------------------------------------------------------
 \begin{abstract}
-This document shows the required format and appearance of a manuscript prepared for SPIE journals.
-It is prepared using LaTeX2e with the class file \texttt{spieman.cls}.
-Please note that the following journals require the use of structured abstracts in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of Medical Imaging}.
-Structured abstracts are encouraged for the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}.
-Guidelines are available on the journal website.
-Whether structured or single-paragraph, the abstract should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting and indexing databases, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-A list of up to six keywords should immediately follow.
+
 \end{abstract}
@@
 % Include email contact information for corresponding author
-{\noindent \footnotesize\textbf{*}Fourth author name,  \linkable{myemail@university.edu} }
+{\noindent \footnotesize\textbf{*}Andrew K. Dunn \linkable{adunn@utexas.edu}}
 
-\begin{spacing}{2}   % use double spacing for rest of manuscript
+\begin{spacing}{2}
 
+% ----------------------------------------------------------------------------------------
+% BEGIN INTRODUCTION SECTION
+% ----------------------------------------------------------------------------------------
 \section{Introduction}
-\label{sect:intro}  % \label{} allows reference to this section
-This document shows the format and appearance of a manuscript prepared for submission to an SPIE journal.
-Note that this template is only intended to be used as a guideline for author convenience.
-It is designed for optimum clarity and ease of reading for editors and reviewers, but the template does not reflect the final page layout of a published journal paper.
-Accepted papers are professionally typeset in XML according to the layout and design of the journal.
+\label{sect:introduction}
 
-\subsection{Use of This Document}
+% ----------------------------------------------------------------------------------------
+% BEGIN METHODS SECTION
+% ----------------------------------------------------------------------------------------
+\section{Methods}
+\label{sect:methods}
 
-This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.
-The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it.
-Authors may use it as a template to create their own manuscript.
-While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.
+% ----------------------------------------------------------------------------------------
+% BEGIN RESULTS SECTION
+% ----------------------------------------------------------------------------------------
+\section{Results}
+\label{sect:results}
 
-\subsection{English}
+% ----------------------------------------------------------------------------------------
+% BEGIN DISCUSSION SECTION
+% ----------------------------------------------------------------------------------------
+\section{Discussion}
+\label{sect:discussion}
 
-Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-In addition, good English usage is essential.
-Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced.
-Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{https://www.editage.com/spie/}.
-SPIE authors will receive a 15\% discount off their services.
-A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission.
-Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.
+% ----------------------------------------------------------------------------------------
+% BEGIN CONCLUSION SECTION
+% ----------------------------------------------------------------------------------------
+\section{Conclusion}
+\label{sect:conclusion}
 
-\subsection{Page Setup and Fonts}
-
-All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm).
-Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.
-
-The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}.
-If this font is not available, use a similar serif font.
-The manuscript should not contain headers or footers.
-Pages should be numbered.
-
-\begin{table}[ht]
-\caption{Fonts sizes and styles.} 
-\label{tab:fonts}
-\begin{center}       
-\begin{tabular}{|l|l|} %% this creates two columns
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
-\hline\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
-\hline 
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Parts of Manuscript}
-
-This section describes the normal structure of a manuscript and how each part should be handled.
-The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
-
-\subsection{Title and Author Information}
-\label{sect:title}
-The article title appears left justified at the top of the first page.
-The title font is 16 pt., bold.
-The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.
-Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.).
-The word ``novel'' should not appear in the title, as publication will imply novelty.
-Avoid the use of acronyms in the title, unless they are widely understood.
-Appendix A contains more about acronyms.
-
-The list of authors immediately follows the title, 18 points below.
-The font is 12 pt., bold and the author names are left justified.
-The author affiliations and addresses follow the names, in 10-pt., normal font and left justified.
-For multiple affiliations, each affiliation should appear on a separate line.
-Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations.
-The corresponding author should be identified with an asterisk, and that person's email address should be provided below the keywords.
-
-\subsection{Abstract}
-The abstract should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting journals, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-Please note that the following journals require the use of structured abstracts in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the\textit{ Journal of Medical Imaging}.
-Structured abstracts are encouraged for the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}.
-Helpful guidelines for structured abstracts are available on the website of the journal.
-
-\subsection{Subject terms/Keywords}
-Keywords are required. Please provide 3-6 keywords related to your paper.
-
-\subsection{Body of Paper}
-The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.
-
-To provide transition elements in your paper, it is important to refer back (or forward) to specific sections.
-Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed...'' or ``Section 2.1 contained a description...'' If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out.
-When occurring in the middle of a sentence, these words are abbreviated Sec., Ref., Eq., and Fig.
-
-At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).
-
-\subsection{Footnotes}
-Textual footnotes should be used rarely to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should generally be avoided.
-If absolutely necessary, the footnote mark must come at the end of a sentence.
-To insert a footnote, use the {\verb|\footnote{}|} command.
-
-\subsection{Appendices}
-Brief appendices may be included when necessary, such as derivations of equations, proofs of theorems, and details of algorithms.
-Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.
-
-\subsection{Disclosures}
-Conflicts of interest should be declared under a separate header, above Acknowledgments.
-If the authors have no competing interests to declare, then a statement should be included declaring no conflicts of interest.
-For assistance generating a disclosure statement, see the form available from  the International Committee of Medical Journal Editors website: \linkable{http://www.icmje.org/conflicts-of-interest/}
-
-\subsection{Acknowledgments}
-Acknowledgments and funding information should be added after the conclusion, and before references.
-Include grant numbers and the full name of the funding body.
-The acknowledgments section does not have a section number.
-
-\subsection{Data, Materials, and Code Availability}
-Availability of data, materials, and/or code used in the research results reported in the manuscript may be declared under the heading "Data, Materials, and Code Availability," following the Acknowledgments section.
-As relevant, provide specific access information or restrictions for data, materials, and computer code (i.e., links to repository access addresses with guidance on commercial or public access).
-
-\subsection{References}
-The References section lists books, articles, and reports that are cited in the paper.
-This section does not have a section number.
-The references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this document.
-
-The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.
-Alternatively, the references may be directly formatted in the LaTeX source file.
-
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.
-References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
-
-The references are numbered in the order of their first citation.
-Citations to the references are made using superscripts, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ...''  Two or more references should be separated by a comma with no space between them.
-Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.
-
-\subsubsection{Reference linking and DOIs}
-A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet.
-The use of DOIs allows readers to easily access cited articles.
-Authors should include the DOI at the end of each reference in brackets if a DOI is available.
-See examples at the end of this manuscript.
-A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}.
-The inclusion of DOIs will facilitate reference linking and is highly recommended.
-
-In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note'' in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}.
-The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.
-
-\subsection{Biographies}
-A brief professional biography of approximately 75 words may be provided for each author, if available.
-Biographies should be placed at the end of the paper, after the references.
-Personal information such as hobbies or birthplace/birthdate should not be included.
-Author photographs are not published.
-
-\section{Section Formatting}
-\label{sect:sections}
-In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
-Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references.
-(Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.
-
-Main section headings are in 12-pt. bold font, left-justified and in title case, where important words are capitalized.
-
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style.
-The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation.
-There is no additional space between paragraphs.
-In LaTeX, paragraphs are separated by blank lines in the source file.
-Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
-
-\subsection{Subsection Headings}
-All important words in a subsection (level 1) header are capitalized.
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end.
-The heading is left justified and its font is 12 pt.
-italic.
-
-\subsubsection{Sub-subsection headings}
-The first word of a sub-subsection is capitalized.
-The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known).
-The heading is left justified and its font is 11 pt.
-italic.
-
-\section{Figures and Tables}
-
-\subsection{Figures}
-
-Figures are numbered in the order in which they are called out in the text.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It may be necessary to move figures or tables around to enhance readability.
-LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.
-
-Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered.
-Figure captions are centered below the figure or graph.
-Figure captions start with the abbreviation ``Fig'' in front of the figure number, followed by a period, and the text in 10-pt.
-font.
-See Fig.~\ref{fig:example} for an example.
-
-\begin{figure}
-\begin{center}
-\begin{tabular}{c}
-\includegraphics[height=5.5cm]{mcr3b.eps}
-\end{tabular}
-\end{center}
-\caption 
-{ \label{fig:example}
-Example of a figure caption. } 
-\end{figure}
-
-Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.
-In no case, should the article's text be wrapped around a figure.
-Figure~\ref{fig:example2} shows two side-by-side images.
-When a figure contains more than one image, the author must submit them as a single image file.
-Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
-\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.
-
-\begin{figure}
-\begin{center}
-\begin{tabular}{c}
-\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
-\\
-(a) \hspace{5.1cm} (b)
-\end{tabular}
-\end{center}
-\caption 
-{ \label{fig:example2}
-Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
-\end{figure}
-
-\subsection{Tables}
-Tables are numbered in the order in which they are referenced.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It is preferable to have tables appear at the top or bottom of the page, if possible.
-Table captions are handled identically to those for figures, except that they appear above the table.
-See Table~\ref{tab:fonts} for an example.
-
-\subsection{Multimedia}
-Acceptable file formats, including MOV (.mov), MPEG (.mpg), and MP4 (.mp4), are playable using standard media players, such as VLC or Windows Media Player.
-The recommended maximum size for each multimedia file is 10-12 MB.
-Authors must insert a representative still image from the video file in the manuscript as a figure.
-The caption label will be linked by the publisher to the actual video file.
-The video may also be mentioned in an existing figure caption.
-Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.
-The video number, file type, and file size should be included in parentheses at the end of the figure caption.
-See Figure \ref{vid:satellite} for an example.
-
-\begin{video}
-\begin{center}
-{\includegraphics[height=5cm]{satellite.eps}}
-\\
-\end{center}
-\caption{\label{vid:satellite}This satellite is a still image from Video 1 (Video 1, MPEG, 2.5 MB).}
-\end{video}
-
-\appendix    % this command starts appendixes
-
-\section{Miscellaneous Formatting Details}
-\label{sect:misc}
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.
-
-\subsection{Formatting Equations}
-Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.
-Important equations appear on their own line.
-Such equations are centered.
-For example, ``The expression for the field of view is
-\begin{equation}
-\label{eq:fov}
-2 a = \frac{(b + 1)}{3c} \, ,
-\end{equation}
-where $a$ is the ...''  Principal equations are numbered, with the equation number placed within parentheses and right justified.
-
-Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma appears after the equation because the next line is a subordinate clause.
-If the equation ends the sentence, a period should follow the equation.
-The line following an equation should not be indented unless it is meant to start a new paragraph.
-Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.
-
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ...'' or ``Combining Eqs.~(2) and (3), we obtain...'' Note that the word ``Equation'' is spelled out if it begins a sentence, but is abbreviated as ``Eq.'' otherwise.
-Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq.'' and the following equation number..
-
-\subsection{Formatting Theorems}
-
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.
-The text of the theorem continues on the same line in normal, 10-pt.
-font, achieved in LaTeX using \verb|\footnotesize|.
-For example,
-
-\vspace{2ex}\noindent{\footnotesize\textbf{Theorem 1.} For any unbiased estimator...}
-
-% \disclosures 
+% ----------------------------------------------------------------------------------------
+% BEGIN DISCLOSURES AND ACKNOWLEDGEMENTS
+% ----------------------------------------------------------------------------------------
 \subsection*{Disclosures}
@@
 
-%%%%% References %%%%%
+% ----------------------------------------------------------------------------------------
+% BEGIN BIBLIOGRAPHY
+% ----------------------------------------------------------------------------------------
+\bibliography{bibliography}
+\bibliographystyle{spiejour}
 
-\bibliography{report}   % bibliography data in report.bib
-\bibliographystyle{spiejour}   % makes bibtex use spiejour.bst
-
-%%%%% Biographies of authors %%%%%
-
+% ----------------------------------------------------------------------------------------
+% AUTHOR BIOGRAPHIES
+% ----------------------------------------------------------------------------------------
+\vspace{1ex}
 \vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering.
@@
 
+% ----------------------------------------------------------------------------------------
+% FIGURE AND TABLE LISTS
+% ----------------------------------------------------------------------------------------
 \listoffigures
@@
 
+% ----------------------------------------------------------------------------------------
+% END
+% ----------------------------------------------------------------------------------------
 \end{spacing}

### 2021-11-11 article.tex
Update template with paper draft

@@
 \usepackage{tocloft}
+\usepackage[version=4]{mhchem}
+\usepackage{booktabs}
+\usepackage{blindtext}
 
@@
 
-\title{SPIE journal papers: sample manuscript showing style and formatting specifications}
+\title{Improved fluid phantom for accurate relative flow calculations for speckle contrast imaging}
 
@@
 \author[a,*]{Andrew K. Dunn}
-\affil[a]{The University of Texas at Austin, Department of Biomedical Engineering, 107 W. Dean Keeton St. Stop C0800, Austin, TX, 78712, USA}
+\affil[a]{Department of Biomedical Engineering, The University of Texas at Austin, Austin, TX, 78712, USA}
 
@@
 \begin{abstract}
-
+Laser speckle contrast imaging (LSCI) is a label-free optical imaging technique that can provide quantitative blood flow data, which can be beneficial during specific neurosurgeries.
+Microfluidic phantoms are commonly used in the development of LSCI systems as they allow for system characterization and ease of hardware optimization.
+In this paper, we demonstrate that pressure-driven flow systems can be used to accurately and precisely control flow changes as small as 2\%, in comparison to the commonly used syringe pump systems that have difficulty resolving changes in flow of 5\%.
+Furthermore, we demonstrate that a multi-exposure speckle imaging (MESI) system is sensitive to small changes in flow and can accurately and repeatably quantify changes in flow as small as 2\%.
+These results indicate that for the characterization and development of LSCI, or MESI, systems, and to mitigate any concerns with the uncertainty in the actual flow-profile and not the hardware itself, pressure-based flow systems should be used with microfluidic channels.
 \end{abstract}
@@
 % Include a list of up to six keywords after the abstract
-\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}
+\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, flow measurement, microfluidic, flow system}
 
@@
 
+Monitoring cerebral blood flow (CBF) is essential during neurosurgery as it provides surgeons with the critical information needed to guide life-saving interventions and is a valuable tool in mitigating post-operative complications \cite{Kirkness.2005}.
+As such, a clinical system that provides continuous CBF monitoring is highly desired.
+Laser speckle contrast imaging (LSCI) is a noninvasive, label-free, optical imaging technique based on coherent dynamic light scattering that has been widely implemented for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}.
+Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution.
+This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and neurosurgical use \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.
+
+Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify the visualization of controlled flow changes in modified systems.
+Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}.
+More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}.
+A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged.
+For applications in rodent studies, 1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}.
+This speed is converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.
+
+Syringe pumps are the most widely used flow control system in microfluidic studies and are commonly believed to provide a highly-controlled flow output.
+A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}.
+However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}.
+Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}.
+The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.
+
+A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor altogether and can provide very stable flow rates \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
+This method involves using compressed air and a pressure regulator to pressurize a reservoir holding the solution, and then applying a controlled pressure to push solution through the microfluidic device at constant flow rates.
+A feedback loop, with an in-line flow measurement device, can be used to adjust the pressure level to achieve a desired flow rate, which allows the user to request a desired flow rate rather than a pressure level.
+
+One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with in vivo absolute flow velocities in animal studies \cite{Kazmi:2013hp}.
+Standard LSCI systems use a single camera exposure time, limiting flow sensitivity to a small range.
+Additionally, several instrumentation factors, namely, illumination variations and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making.
+An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}.
+MESI has been shown to be reliable for chronic imaging and to have high correlation with in vivo absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons.
+By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.
+
+In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regularized flow system.
+By understanding the associated uncertainty with each system, we can provide insight on the experimental design for a microfluidic study that aims to assess the hardware performance of an optical system, without fear that performance can be compromised due to flow-related noise.
+Quantifying this error allows us to accurately determine the true sensitivity to relative flow changes of a MESI system.
+Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%.
+The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.
+
+The remainder of the paper can be summarized as follows: Section \ref{sect:methods} describes the microfluidic phantom fabrication and the different experimental tests to assess the uncertainty with the syringe pump and pressure regulated systems, the instrumentation for the MESI system, and the mathematical formulation necessary to calculate relative flow from the data collected with the MESI system.
+Results from these experimental protocols, namely the uncertainty analysis and the MESI flow calculations, are presented in Section \ref{sect:results}.
+Lastly, the paper findings and contributions are summarized in Section \ref{sect:discussion}.
+
 % ----------------------------------------------------------------------------------------
@@
 \label{sect:methods}
+
+\subsection{Microfluidic Phantom Fabrication}
+The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) per gram of PDMS added to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
+The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom.
+Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.
+
+A machined aluminum mold was used to cast the microchannel, shown in Fig.~\ref{fig:microfluidic}a.
+The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the microfluidic channel.
+A square cross-section (1:1 aspect ratio) was desired to match the aspect ratio of the circular cross-section vascular geometries in vivo.
+The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring.
+The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold.
+The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel.
+Inlet and outlet ports were attached using 23G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
+Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was used to connect to the blunt tip ports as inlet and outlet tubing.
+The inlet tubing was connected to the flow sensor and the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.).
+The outlet tubing drained into a vial, with the tubing end submerged in solution.
+A photograph of the finished phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS and the glass slide seals the surface.
+
+% Figure 1 - Microfluidic Flow Phantom
+\begin{figure}
+    \includegraphics[width=\textwidth]{Figure1.pdf}
+    \caption {
+        (a) Photograph of the machined aluminum mold with a 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, extrusion used to cast the PDMS during fabrication of the microfluidic flow phantom.
+(b) Photograph of the finished microfluidic flow phantom, showing PDMS bonded to a glass slide, with inlet and outlet ports secured using epoxy.
+Tubing was secured to the ports and connected with the rest of the system using fluidic fittings.
+    }
+    \label{fig:microfluidic}
+\end{figure}
+
+A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution.
+Based on Ref.
+\cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit = 0.5 is approximately 20 cm$^{-1}$.
+By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of by 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$.
+However, we note that the anisotropy of the microspheres in our solution is different that that of whole blood ($g = 0.92$ compared to $g = 0.98$).
+The blood-mimicking solution was preferred over whole blood for several reasons, namely: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water flow.
+Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid.
+The solution of microspheres was freshly mixed before each experiment to reduce aggregation of particles in the dilution.
+Once mixed, the solution was sonicated (10 minutes) to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.
+
+\subsection{Microfluidic Flow System Instrumentation}
+
+To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel.
+A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system}a.
+The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) recorded the absolute flow rate.
+
+The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution.
+The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output (10 mL = 14.5 mm).
+It should be noted that a 3 mL syringe was also tested, however its performance was significantly worse than the 10 mL syringe and, in some cases, could not resolve the desired flow profiles.
+
+The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system}c.
+This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with blood-mimicking solution.
+Prior to running the desired flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure.
+The pressure control system used built-in software (MAESFLO) to provide feedback from the inline flow sensor to regulate the pressure to achieve the desired flow rate.
+
+\subsection{Microfluidic Flow System Assessment}
+
+Two stepped flow profile experiments were conducted to assess each flow system.
+First, a 3-step flow profile was used to determine the uncertainty of each flow control system.
+The experiment lasted 240 seconds, beginning with 30 seconds of no flow (0 mm/s) followed by one full minute at each flow speed (2.4, 3.6, and 4.8 mm/s) before concluding with an additional 30 seconds of no flow.
+The experiment was repeated three times on each system.
+The second flow profile experiment consisted of a 13-step flow profile.
+The flow speed was once again varied from 2.4 to 4.8 mm/s, however in smaller 0.2 mm/s increments.
+As with the first experiment, the flow profile begins and ends with 30 seconds of no flow, with one full minute at each programmed flow speed (840 seconds total duration).
+The second experiment was also repeated three times on each flow control system.
+
+To quantify and compare each system, we calculated the total combined uncertainty in accordance with National Institute of Standards and Technology (NIST) guidelines \cite{Taylor.199438,NIST:2002}.
+Three main sources of uncertainty were identified for inclusion in the uncertainty budget: repeatability, reproducibility, and measurement bias.
+Standard uncertainties were calculated for each flow step using 55 seconds of data, allowing for 5 seconds of transition from the previous flow state.
+All values were expressed as percentages relative to their respective means.
+
+The uncertainty in repeatability, which is a measure of within-run variance, was defined as:
+%
+% Equation 1 - Uncertainty in Repeatability
+\begin{equation}
+    \label{eq:u_repeat}
+    u_\textnormal{repeat} = 100 \times \frac{s_p}{\bar{x}}
+\end{equation}
+
+\noindent where $s_p^2$ is the pooled variance across the three trials at each flow speed and $\bar{x}$ is the mean value of the measured flow speed across all trials.
+
+The uncertainty in reproducibility, which is a measure of between-run variance, was defined as:
+%
+% Equation 2 - Uncertainty in Reproducibility
+\begin{equation}
+    \label{eq:u_reproduce}
+    u_\textnormal{reproduce} = 100 \times \frac{s}{\bar{x}}
+\end{equation}
+
+\noindent where $s^2$ is the variance in the mean flow speed across all three trials and $\bar{x}$ is the mean value of the measured flow speed across all trials.
+
+Finally, the uncertainty in measurement bias, was defined as:
+%
+% Equation 3 - Uncertainty in Bias
+\begin{equation}
+    \label{eq:u_bias}
+    u_\textnormal{bias} = 100 \times \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
+\end{equation}
+
+\noindent where $\bar{x}$ is the mean value of the measured flow speed across all trials and $x_{ref}$ is the programmed flow speed (2.4, 3.6, or 4.8 mm/s) at each step.
+
+The total combined standard uncertainty ($u_c$) was then calculated using the root sum of squares of the individual uncertainty components and reported as the expanded uncertainty ($U=ku_c$) with a $k=2$ coverage factor corresponding to a level of confidence of approximately 95\%.
+
+\subsection{MESI Instrumentation}
+
+A schematic of the imaging setup is shown in Fig.~\ref{fig:system}a.
+MESI was performed \cite{Parthasarathy:2008el} using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.).
+The operating current on the laser diode controller (LDC205C, Thorlabs, Inc.) was fixed at 380 mA (300 mW) and the target temperature set to 25 $^\circ$C on the temperature controller (TED200C, Thorlabs, Inc.).
+The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance.
+Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam.
+The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the sample.
+
+A pair of consumer camera lenses were used to image the scattered light (AF Nikkor 50 mm $f$/1.8D + AF Micro-Nikkor 105 mm $f$/2.8D, Nikon Corp.) with 2.1$\times$ magnification through a bandpass filter (785$\pm$31 nm, 87-773, Edmund Optics Inc.) to a CMOS camera (acA1920-155um, 1920 $\times$ 1200 pixels, Basler AG).
+Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm.
+The camera exposures were temporally synchronized with the modulated laser pulses.
+Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of $\sim$2.5 frames-per-second (fps).
+The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
+The entire acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.
+
+% Figure 2 - System Schematic
+\begin{figure}
+    \includegraphics[width=\textwidth]{Figure2.pdf}
+    \caption {
+        (a) Optical system schematic for microfluidic flow assessment.
+A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements.
+Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system.
+The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
+    }
+    \label{fig:system}
+\end{figure}
+
+\subsection{MESI Microfluidic Flow Measurements}
+
+A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of MESI.
+The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments.
+Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile.
+MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps).
+Because the flow sensor software used a separate clock than the MESI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step.
+The experiment was repeated a total of four times across two days.
+
+Raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) using a 7$\times$7-pixel sliding window.
+The average speckle contrast of each frame was then calculated within a region centered in the microfluidic channel and used to estimate the correlation time ($\tau_c$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}.
+The averaged speckle contrast values were fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} using all fifteen exposure times to obtain $\tau_c$:
+%
+% Equation 1 - MESI Equation
+\begin{equation}
+    \label{eq:mesi}
+    K^2(T,\tau_c) =
+        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
+        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
+        \nu
+\end{equation}
+
+\noindent where $T$ is the camera exposure time, $x=T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu$ represents exposure-independent instrument noise and nonergodic variances.
+$\beta$ was held constant at all timepoints by performing an initial fit to Eq.
+3 using the median speckle contrast value at each exposure across the entire multi-exposure dataset.
+All fitting was performed with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in MATLAB (R2021a, MathWorks, Inc.).
+The resulting $\tau_c$ estimates were smoothed temporally using a central moving average filter ($k=5$).
+
+Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used to visualize measurements.
+In order to directly compare the MESI measurements with the flow sensor, the relative flow was calculated using the average value of the 1 mm/s step as the baseline ($rICT = ICT/ICT_\textnormal{1mm/s}$).
+The average value of each flow step was calculated using 115 seconds of data, allowing for 5 seconds of transition from the previous step.
 
@@
 
+\subsection{Microfluidic Flow System Assessment}
+
+A comparison between the measured flow speeds of the syringe pump and the pressure-regulated flow system is shown in Fig.~\ref{fig:syringe_vs_pressure}.
+From these plots, we observe that the pressure-regulated system outperforms the syringe pump system by accurately and steadily reaching the programmed flow speeds in both experiments.
+While both systems quickly responded to the desired flow changes (Fig.~\ref{fig:syringe_vs_pressure}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated system.
+Furthermore, the small flow step experiment (Fig.~\ref{fig:syringe_vs_pressure}b) demonstrated that the syringe pump system cannot reliably produce finer flow changes as seen by the loss of the stair-stepped flow pattern.
+
+% Figure 3 - Syringe Pump vs. Pressure System
+\begin{figure}
+    \includegraphics[width=\textwidth]{Figure3.pdf}
+    \caption {
+        Flow profiles for the syringe pump (blue) and pressure-regulated (red) flow systems compared to the ideal programmed flow (black) for one run of the (a) 3-step and (b) 13-step experiments.
+The microfluidic flow speed varied between 2.4 to 4.8 mm/s in 1.2 mm/s and 0.2 mm/s steps for the 3- and 13-step experiments, respectively.
+    }
+    \label{fig:syringe_vs_pressure}
+\end{figure}
+
+Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiment.
+These results confirm the observations from Fig.~\ref{fig:syringe_vs_pressure} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds.
+The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}.
+These results provide evidence of the superiority of the pressure-regulated flow system, particularly when attempting to produce small flow changes.
+With the syringe pump system, it would be impossible to reliably separate changes in relative flow of 20\% from flow system noise at the 2.4 mm/s flow speed.
+This magnitude of uncertainty in flow generation would make it difficult to assess an optical system’s ability to detect small changes in flow.
+This limitation is visually represented in Fig.~\ref{fig:syringe_vs_pressure}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes.
+Using the pressure-regulated flow system, we can confidently design experiments with relative flow changes of only 1.5\% and be certain that the resulting optical system measurements are not due to flow system noise.
+Furthermore, this would allow for the assessment of improvements to optical system performance at this scale.
+
+\begin{table}
+    \caption {
+        Standard uncertainties for repeatability, reproducibility, and bias by flow speeds for the syringe pump and pressure-regulated flow systems.
+    }
+    \label{tab:uncertainty_standard}
+    \centering
+    \begin{tabular}{rccccccccc}
+        \addlinespace
+        \toprule
+            &
+            \multicolumn{3}{c}{$\boldsymbol{u_\textbf{repeat}}$ (\%)}       & 
+            \multicolumn{3}{c}{$\boldsymbol{u_\textbf{reproduce}}$ (\%)}    & 
+            \multicolumn{3}{c}{$\boldsymbol{u_\textbf{bias}}$ (\%)}         \\
+            \cmidrule(lr){2-4}
+            \cmidrule(lr){5-7}
+            \cmidrule(lr){8-10}
+        \textbf{Flow Speed (mm/s)} & 2.4    & 3.6   & 4.8   & 2.4   & 3.6   & 4.8   & 2.4   & 3.6   & 4.8   \\
+        \midrule
+        \textbf{Syringe Pump}      & 1.31   & 0.90  & 1.86  & 4.01  & 2.15  & 1.07  & 10.3  & 1.80  & 2.55  \\
+        \textbf{Pressure System}   & 0.55   & 0.45  & 0.39  & 0.002 & 0.009 & 0.003 & 0.03  & 0.07  & 0.03  \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\begin{table}
+    \caption {
+        Combined and expanded uncertainties (with $k=2$ coverage) by flow speeds for the syringe pump and pressure-regulated flow systems.
+    }
+    \label{tab:uncertainty_combined}
+    \centering
+    \begin{tabular}{rcccccc}
+        \addlinespace
+        \toprule
+            &
+            \multicolumn{3}{c}{$\boldsymbol{u_c}$ (\%)}     &
+            \multicolumn{3}{c}{$\boldsymbol{U}$ (\%)}       \\
+            \cmidrule(lr){2-4}
+            \cmidrule(lr){5-7}
+        \textbf{Flow Speed (mm/s)} & 2.4    & 3.6   & 4.8   & 2.4   & 3.6   & 4.8   \\
+        \midrule
+        \textbf{Syringe Pump}      & 11.1   & 2.94  & 3.34  & 22.2  & 5.89  & 6.68  \\
+        \textbf{Pressure System}   & 0.56   & 0.45  & 0.39  & 1.11  & 0.91  & 0.77  \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\subsection{MESI Microfluidic Flow Measurements}
+
+The MESI microfluidic flow measurements using only the pressure-regulated flow system are shown in Fig.~\ref{fig:mesi_flow}.
+The relative flow measured by MESI ($rICT$) is plotted alongside the relative flow sensor measurements from a single trial in Fig.~\ref{fig:mesi_flow}a.
+Both metrics were calculated using the average of the first flow step (1 mm/s) as the baseline.
+Data for each flow step were pooled and averaged across all four trials to assess the overall performance of MESI as seen in Fig.~\ref{fig:mesi_flow}b.
+The coefficient of determination ($R^2$) and concordance correlation coefficient ($\rho_c$) \cite{Lin.1989} were 0.988 and 0.994, respectively, indicating strong agreement between the MESI $rICT$ and the flow sensor measurements.
+The absolute MESI $ICT$ measurements are also plotted on Fig.~\ref{fig:mesi_flow}b and exhibit the same linearity with microfluidic flow speed.
+
+% Figure 4 - MESI Flow Measurements
+\begin{figure}
+    \includegraphics[width=\textwidth]{Figure4.pdf}
+    \caption {
+        (a) Relative flow profiles for the flow sensor (black) and MESI (red) for one trial, both normalized to the average of the first flow step (1 mm/s).
+(b) Performance of MESI flow estimates (relative and absolute) compared to measured microfluidic flow speed aggregated across all four trials (mean $\pm$ sd).
+The dashed line denotes the line of equality indicative of a 1:1 relationship.
+    }
+    \label{fig:mesi_flow}
+\end{figure}
+
+Fig.~\ref{fig:mesi_error} presents the percent error for the MESI measurements at each flow step aggregated across all four trials.
+The absolute error was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it almost doubled in value.
+
+% Figure 5 - MESI Error
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{Figure5.pdf}
+    \caption {
+        Percent error for MESI $rICT$ measurements at each flow step relative to the flow sensor measurements.  Data aggregated by flow step across all four trials.
+    }
+    \label{fig:mesi_error}
+\end{figure}
+
 % ----------------------------------------------------------------------------------------
@@
 \label{sect:discussion}
+
+\blindtext
 
@@
 
+This paper demonstrates that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of optical imaging systems using microfluidics.
+We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds.
+Furthermore, we demonstrate that MESI can be used to detect changes in relative flow as small as 5\%.
+Given the large uncertainties associated with syringe pump systems, it would be impossible to determine that such a measurement arose from an actual flow change rather than random or systematic error.
+These results indicate that it is necessary to use a pressure-regulated flow system in order to properly assess the performance of a MESI system or when characterizing hardware changes to such a system.
+
 % ----------------------------------------------------------------------------------------
@@
 \subsection*{Disclosures}
-Conflicts of interest should be declared under a separate header.
-If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.
+A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.
 
-\subsection* {Acknowledgments}
-This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
+\subsection*{Author Contributions}
+C.T.S.
+and L.M.R.
+constructed the imaging system, conceived the experiments, and acquired the data.
+C.T.S., A.S., and L.M.R.
+analyzed the results and wrote the manuscript.
+A.K.D.
+supervised the project.
+All authors contributed to the manuscript revisions.
+
+\subsection*{Acknowledgments}
+This study was supported by the National Institutes of Health (Nos. ?)
 
 \subsection* {Data, Materials, and Code Availability} 
-As relevant, the availability of data, materials, and/or software code used in the research results reported in the manuscript may be declared in this section.
-(Note: this section is required for the \textit{Journal of Biomedical Optics} and \textit{Neurophotonics}.) Provide specific access information or restrictions for data, materials, and computer code (i.e., links to repository access addresses with guidance on commercial or public access).
+The code and data that support the findings of this study are available from the corresponding author, A.K.D., upon reasonable request.
 

### 2022-02-01 article.tex
Incorporate Andy text edits

@@
 \usepackage{blindtext}
+\usepackage{xcolor}
 
@@
 
-Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify the visualization of controlled flow changes in modified systems.
+Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify controlled flow changes in well-defined channels.
 Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}.
@@
 A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged.
-For applications in rodent studies, 1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}.
+For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}.
 This speed is converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.
@@
 Syringe pumps are the most widely used flow control system in microfluidic studies and are commonly believed to provide a highly-controlled flow output.
-A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}.
+\textcolor{red}{A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps}; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}.
 However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}.
@@
 
-In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regularized flow system.
+In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regulated flow system.
 By understanding the associated uncertainty with each system, we can provide insight on the experimental design for a microfluidic study that aims to assess the hardware performance of an optical system, without fear that performance can be compromised due to flow-related noise.
 Quantifying this error allows us to accurately determine the true sensitivity to relative flow changes of a MESI system.
-Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%.
-The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.
-
-The remainder of the paper can be summarized as follows: Section \ref{sect:methods} describes the microfluidic phantom fabrication and the different experimental tests to assess the uncertainty with the syringe pump and pressure regulated systems, the instrumentation for the MESI system, and the mathematical formulation necessary to calculate relative flow from the data collected with the MESI system.
-Results from these experimental protocols, namely the uncertainty analysis and the MESI flow calculations, are presented in Section \ref{sect:results}.
-Lastly, the paper findings and contributions are summarized in Section \ref{sect:discussion}.
+\textcolor{red}{Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%.} The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.
 
@@
     \label{eq:u_repeat}
-    u_\textnormal{repeat} = 100 \times \frac{s_p}{\bar{x}}
+    u_\textnormal{repeat} = 100\left(\frac{s_p}{\bar{x}}\right)
 \end{equation}
@@
     \label{eq:u_reproduce}
-    u_\textnormal{reproduce} = 100 \times \frac{s}{\bar{x}}
+    u_\textnormal{reproduce} = 100\left(\frac{s}{\bar{x}}\right)
 \end{equation}
@@
     \label{eq:u_bias}
-    u_\textnormal{bias} = 100 \times \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
+    u_\textnormal{bias} = 100 \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
 \end{equation}

### 2022-02-17 article.tex
Significant revisions
Two major points of paper: 1) pressure-regulated flow systems outperform syringe pumps 2) Evaluating LSCI vs. MESI using pressure-regulated flow system

@@
 
-\title{Improved fluid phantom for accurate relative flow calculations for speckle contrast imaging}
+\title{Using pressure-driven flow systems to evaluate laser speckle contrast imaging}
 
@@
 
-One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with in vivo absolute flow velocities in animal studies \cite{Kazmi:2013hp}.
+One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}.
 Standard LSCI systems use a single camera exposure time, limiting flow sensitivity to a small range.
@@
 An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}.
-MESI has been shown to be reliable for chronic imaging and to have high correlation with in vivo absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons.
+MESI has been shown to be reliable for chronic imaging and to have high correlation with \textit{in vivo} absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons.
 By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.
@@
 \subsection{Microfluidic Phantom Fabrication}
+\label{sect:methods_phantom}
 The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) per gram of PDMS added to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
@@
 
-A machined aluminum mold was used to cast the microchannel, shown in Fig.~\ref{fig:microfluidic}a.
-The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the microfluidic channel.
-A square cross-section (1:1 aspect ratio) was desired to match the aspect ratio of the circular cross-section vascular geometries in vivo.
+A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a.
+The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel.
+The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}.
 The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring.
@@
 To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel.
-A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system}a.
-The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) recorded the absolute flow rate.
+A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a.
+The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) was used to record the absolute flow rate.
+All flow sensor measurements were downsampled from 10 Hz to 2 Hz using interpolation to match the timing of the optical measurements.
 
-The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution.
-The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output (10 mL = 14.5 mm).
+The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system_lsci}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution as described in Section \ref{sect:methods_phantom}.
+The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output.
 It should be noted that a 3 mL syringe was also tested, however its performance was significantly worse than the 10 mL syringe and, in some cases, could not resolve the desired flow profiles.
 
-The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system}c.
-This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with blood-mimicking solution.
-Prior to running the desired flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure.
+The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system_lsci}c.
+This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution.
+Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure.
 The pressure control system used built-in software (MAESFLO) to provide feedback from the inline flow sensor to regulate the pressure to achieve the desired flow rate.
 
+% Figure 2 - LSCI System Schematic + Syringe Pump and Pressure Flow System
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\textwidth]{Figure2.pdf}
+    \caption {
+        (a) LSCI system schematic for microfluidic flow assessment.
+A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements.
+Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system.
+The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
+    }
+    \label{fig:system_lsci}
+\end{figure}
+
 \subsection{Microfluidic Flow System Assessment}
+\label{sect:methods_flow_assess}
 
-Two stepped flow profile experiments were conducted to assess each flow system.
+Two stepped flow profile experiments were conducted to assess each flow system using the commercial flow sensor.
 First, a 3-step flow profile was used to determine the uncertainty of each flow control system.
@@
 
-To quantify and compare each system, we calculated the total combined uncertainty in accordance with National Institute of Standards and Technology (NIST) guidelines \cite{Taylor.199438,NIST:2002}.
+To quantify and compare each flow system, we calculated the total combined uncertainty in accordance with National Institute of Standards and Technology (NIST) guidelines \cite{Taylor.199438,NIST:2002}.
 Three main sources of uncertainty were identified for inclusion in the uncertainty budget: repeatability, reproducibility, and measurement bias.
@@
 
+\subsection{LSCI Instrumentation}
+
+A schematic of the LSCI setup is shown in Fig.~\ref{fig:system_lsci}a.
+Measurements were performed using a 660 nm laser diode (HL6545MG, Thorlabs Inc.) mounted in a temperature-controlled housing (LDM21, Thorlabs Inc.) and expanded using an aspheric lens to obliquely illuminate the microfluidic.
+The laser diode controller (LDC205C, Thorlabs, Inc.) was set to 200 mA ($\sim$120 mW) while the temperature controller (TED200C, Thorlabs Inc.) was set to 10.5 k$\Omega$ (23.8 $^\circ$C).
+A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging.
+\textcolor{red}{Is there a filter?
+Specifics of f-number and speckle size?} The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++.
+The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm.
+The camera exposure time was set to 0.5 ms and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps).
+\textcolor{red}{Explanation for 0.5 ms exposure time?}
+
+\subsection{LSCI Flow Measurements}
+\label{sect:methods_lsci}
+
+To validate the flow sensor measurements, single-exposure LSCI was used to simultaneously image the microfluidic flow phantom during the 13-step flow experiments described in Section \ref{sect:methods_flow_assess}.
+Raw intensity images were converted to speckle contrast images using Eq.
+\ref{eq:sc}, where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) in a sliding 7$\times$7-pixel window centered at every pixel.
+%
+% Equation 4 - Speckle Contrast
+\begin{equation}
+    \label{eq:sc}
+    K = \frac{\sigma_{s}}{\langle{I}\rangle}
+\end{equation}
+
+By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time.
+\textcolor{red}{Unclear if there was additional averaging performed by the Speckle Software (i.e.
+frames/sequence=15?
+Was the saved SC data already averaged?)} During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel.
+This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}.
+The averaged speckle contrast value at each timepoint was fitted for its corresponding $\tau_{c}$ using Eq.
+\ref{eq:lsci},
+%
+% Equation 5 - LSCI Equation
+\begin{equation}
+    \label{eq:lsci}
+    K^2(T, \tau_{c}) = \beta\frac{e^{-2x}-1+2x}{2x^2}
+\end{equation}
+
+\noindent where $T$ is the camera exposure time, $x=T/\tau_{c}$, and $\beta$ is an instrumentation factor that accounts for
+speckle sampling, polarization, and coherence effects \cite{Bandyopadhyay:2005bg}.
+For these measurements, it was assumed that $\beta=1$, which exclusively allows for the computation of relative flow changes.
+The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).
+
+Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used for visualization.
+In order to compare the LSCI measurements with the flow sensor, the relative flow for each technique was calculated using the average value of the first step (2.4 mm/s) as the baseline.
+The initial rise of the first flow step was also used to synchronize the timing of the two datasets.
+
 \subsection{MESI Instrumentation}
 
-A schematic of the imaging setup is shown in Fig.~\ref{fig:system}a.
+A schematic of the MESI setup is shown in Fig.~\ref{fig:system_mesi}.
 MESI was performed \cite{Parthasarathy:2008el} using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.).
@@
 The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance.
-Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam.
-The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the sample.
+Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled \textcolor{red}{(Which lens?)} into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam.
+The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the microfluidic.
 
@@
 The camera exposures were temporally synchronized with the modulated laser pulses.
-Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of $\sim$2.5 frames-per-second (fps).
+Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of approximately 2.5 fps.
 The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
@@
 
-% Figure 2 - System Schematic
+% Figure 3 - MESI System Schematic
 \begin{figure}
-    \includegraphics[width=\textwidth]{Figure2.pdf}
+    \centering
+    \includegraphics[width=0.75\textwidth]{Figure3.pdf}
     \caption {
-        (a) Optical system schematic for microfluidic flow assessment.
-A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements.
-Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system.
-The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
+        System schematic for microfluidic flow assessment of MESI and LSCI with the pressure-regulated flow system.
     }
-    \label{fig:system}
+    \label{fig:system_mesi}
 \end{figure}
 
-\subsection{MESI Microfluidic Flow Measurements}
+\subsection{MESI and LSCI Performance}
 
-A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of MESI.
+A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI.
 The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments.
@@
 MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps).
+Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}.
 Because the flow sensor software used a separate clock than the MESI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step.
@@
 
-Raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) using a 7$\times$7-pixel sliding window.
-The average speckle contrast of each frame was then calculated within a region centered in the microfluidic channel and used to estimate the correlation time ($\tau_c$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}.
-The averaged speckle contrast values were fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} using all fifteen exposure times to obtain $\tau_c$:
+The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described in Section \ref{sect:methods_lsci}.
+The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
 %
-% Equation 1 - MESI Equation
+% Equation 6 - MESI Equation
 \begin{equation}
@@
 \noindent where $T$ is the camera exposure time, $x=T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu$ represents exposure-independent instrument noise and nonergodic variances.
-$\beta$ was held constant at all timepoints by performing an initial fit to Eq.
-3 using the median speckle contrast value at each exposure across the entire multi-exposure dataset.
+$\beta$ was held constant at all timepoints during an experiment by performing an initial fit to Eq.
+\ref{eq:mesi} using the median speckle contrast value at each exposure across the entire multi-exposure dataset.
 All fitting was performed with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in MATLAB (R2021a, MathWorks, Inc.).
-The resulting $\tau_c$ estimates were smoothed temporally using a central moving average filter ($k=5$).
+The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).
 
-Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used to visualize measurements.
-In order to directly compare the MESI measurements with the flow sensor, the relative flow was calculated using the average value of the 1 mm/s step as the baseline ($rICT = ICT/ICT_\textnormal{1mm/s}$).
-The average value of each flow step was calculated using 115 seconds of data, allowing for 5 seconds of transition from the previous step.
+In order to directly compare the MESI and single-exposure LSCI measurements with the flow sensor, the relative flow was calculated using the average value of the first step (1 mm/s) as the baseline.
+The average values for each flow step were calculated using 115 seconds of data, allowing for 5 seconds of transition from the previous step.
 
@@
 
-A comparison between the measured flow speeds of the syringe pump and the pressure-regulated flow system is shown in Fig.~\ref{fig:syringe_vs_pressure}.
-From these plots, we observe that the pressure-regulated system outperforms the syringe pump system by accurately and steadily reaching the programmed flow speeds in both experiments.
-While both systems quickly responded to the desired flow changes (Fig.~\ref{fig:syringe_vs_pressure}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated system.
-Furthermore, the small flow step experiment (Fig.~\ref{fig:syringe_vs_pressure}b) demonstrated that the syringe pump system cannot reliably produce finer flow changes as seen by the loss of the stair-stepped flow pattern.
+The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor is shown in Fig.~\ref{fig:SvP-FS}.
+These plots demonstrate that the pressure-regulated system outperforms the syringe pump by accurately and steadily matching the programmed flow speeds across both experiments.
+While both flow systems responded quickly to the desired flow changes during the large step size experiment (Fig.~\ref{fig:SvP-FS}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated system.
+Furthermore, the small step size experiment (Fig.~\ref{fig:SvP-FS}b) demonstrated that the syringe pump system could not reliably reproduce the finer flow changes as evidenced by the loss of the stair-stepped flow pattern.
 
-% Figure 3 - Syringe Pump vs. Pressure System
+% Figure 4 - Syringe Pump vs. Pressure System (Flow Sensor only)
 \begin{figure}
-    \includegraphics[width=\textwidth]{Figure3.pdf}
+    \includegraphics[width=\textwidth]{Figure4.pdf}
     \caption {
-        Flow profiles for the syringe pump (blue) and pressure-regulated (red) flow systems compared to the ideal programmed flow (black) for one run of the (a) 3-step and (b) 13-step experiments.
+        Flow sensor measurements for the syringe pump (blue) and pressure-regulated (red) flow systems compared to the ideal programmed flow (black) for one run of the (a) 3-step and (b) 13-step experiments.
 The microfluidic flow speed varied between 2.4 to 4.8 mm/s in 1.2 mm/s and 0.2 mm/s steps for the 3- and 13-step experiments, respectively.
     }
-    \label{fig:syringe_vs_pressure}
+    \label{fig:SvP-FS}
 \end{figure}
@@
 Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiment.
-These results confirm the observations from Fig.~\ref{fig:syringe_vs_pressure} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds.
+These results confirm the observations from Fig.~\ref{fig:SvP-FS} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds.
 The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}.
@@
 With the syringe pump system, it would be impossible to reliably separate changes in relative flow of 20\% from flow system noise at the 2.4 mm/s flow speed.
-This magnitude of uncertainty in flow generation would make it difficult to assess an optical system’s ability to detect small changes in flow.
-This limitation is visually represented in Fig.~\ref{fig:syringe_vs_pressure}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes.
-Using the pressure-regulated flow system, we can confidently design experiments with relative flow changes of only 1.5\% and be certain that the resulting optical system measurements are not due to flow system noise.
-Furthermore, this would allow for the assessment of improvements to optical system performance at this scale.
+This magnitude of uncertainty in flow generation would make it difficult to assess an optical system's ability to detect small changes in flow.
+This limitation is visually represented in Fig.~\ref{fig:SvP-FS}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes.
+Using the pressure-regulated flow system, experiments could be designed with relative flow changes of only 1.5\% while remaining confident that the resulting optical system measurements were not caused by flow system noise.
+This level of certainty would also permit assessing improvements to optical system performance at this scale.
 
@@
 
-\subsection{MESI Microfluidic Flow Measurements}
+\subsection{LSCI Flow Measurements}
 
-The MESI microfluidic flow measurements using only the pressure-regulated flow system are shown in Fig.~\ref{fig:mesi_flow}.
-The relative flow measured by MESI ($rICT$) is plotted alongside the relative flow sensor measurements from a single trial in Fig.~\ref{fig:mesi_flow}a.
-Both metrics were calculated using the average of the first flow step (1 mm/s) as the baseline.
-Data for each flow step were pooled and averaged across all four trials to assess the overall performance of MESI as seen in Fig.~\ref{fig:mesi_flow}b.
-The coefficient of determination ($R^2$) and concordance correlation coefficient ($\rho_c$) \cite{Lin.1989} were 0.988 and 0.994, respectively, indicating strong agreement between the MESI $rICT$ and the flow sensor measurements.
-The absolute MESI $ICT$ measurements are also plotted on Fig.~\ref{fig:mesi_flow}b and exhibit the same linearity with microfluidic flow speed.
+The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and LSCI is shown in Fig.~\ref{fig:SvP-FS_LSCI}.
+The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step.
+The relative flow changes measured by LSCI closely track those of the flow sensor and corroborate the accuracy and stability issues seen with the syringe pump system.
+These results also demonstrate that LSCI is capable of detecting similar changes in flow as the commercial flow sensor for relative flow changes up to double the baseline \textcolor{red}{(awkward wording)}.
 
-% Figure 4 - MESI Flow Measurements
+% Figure 5 - Syringe Pump vs. Pressure System (Flow Sensor + LSCI)
 \begin{figure}
-    \includegraphics[width=\textwidth]{Figure4.pdf}
+    \includegraphics[width=\textwidth]{Figure5.pdf}
     \caption {
-        (a) Relative flow profiles for the flow sensor (black) and MESI (red) for one trial, both normalized to the average of the first flow step (1 mm/s).
-(b) Performance of MESI flow estimates (relative and absolute) compared to measured microfluidic flow speed aggregated across all four trials (mean $\pm$ sd).
-The dashed line denotes the line of equality indicative of a 1:1 relationship.
+        Relative flow measurements for the (a) syringe pump and (b) pressure-regulated flow systems as measured with the flow sensor (blue) and single-exposure LSCI (red).
+All measurements were normalized to the average of the first flow step (2.4 mm/s) and compared to the ideal programmed flow (black).
     }
-    \label{fig:mesi_flow}
+    \label{fig:SvP-FS_LSCI}
 \end{figure}
 
-Fig.~\ref{fig:mesi_error} presents the percent error for the MESI measurements at each flow step aggregated across all four trials.
-The absolute error was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it almost doubled in value.
+\subsection{MESI and LSCI Performance}
 
-% Figure 5 - MESI Error
+The flow measurement performance assessment using the pressure-regulated flow system is shown in Fig.~\ref{fig:flow_mesi_lsci}.
+The relative flow measured by MESI and LSCI are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a.
+All relative flows were calculated using the average of the first flow step (1 mm/s) as the baseline.
+Data for each flow step were pooled and averaged across all four trials to assess the overall performance as seen in Fig.~\ref{fig:flow_mesi_lsci}b.
+The coefficients of determination ($R^2$) for this averaged MESI and LSCI data relative to the flow sensor were 0.988 and 0.839, respectively.
+The concordance correlation coefficients ($\rho_c$), a metric designed to evaluate reproducibility \cite{Lin.1989}, were 0.994 and 0.908, respectively.
+These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI increasingly outperforms LSCI across large changes in relative flow.
+
+% Figure 6 - LSCI + MESI Flow Measurements
+\begin{figure}
+    \includegraphics[width=\textwidth]{Figure6.pdf}
+    \caption {
+        (a) Relative flow profiles for the flow sensor (black), LSCI (blue), and MESI (red) for one trial, all normalized to the average of the first flow step (1 mm/s).
+(b) Performance of LSCI and MESI flow estimates compared to measured microfluidic flow speed aggregated across all four trials (mean $\pm$ sd).
+The dashed line denotes the line of equality indicative of a linear 1:1 relationship.
+    }
+    \label{fig:flow_mesi_lsci}
+\end{figure}
+
+Fig.~\ref{fig:error} summarizes the accuracy of the MESI and LSCI measurements at each flow step aggregated across all four trials.
+The absolute error for MESI was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it increased to almost 9\%.
+In contrast, the LSCI error was over 8\% for all flow speeds, increasing to over 17\% for flow speeds greater than 4 mm/s.
+
+% Figure 7 - LSCI + MESI Error
 \begin{figure}
     \centering
-    \includegraphics[width=0.5\textwidth]{Figure5.pdf}
+    \includegraphics[width=0.75\textwidth]{Figure7.pdf}
     \caption {
-        Percent error for MESI $rICT$ measurements at each flow step relative to the flow sensor measurements.  Data aggregated by flow step across all four trials.
+        Percent error for LSCI (blue) and MESI (red) measurements at each flow step relative to the corresponding flow sensor measurements.
+Data aggregated by flow step and averaged across all four trials.
     }
-    \label{fig:mesi_error}
+    \label{fig:error}
 \end{figure}
@@
 supervised the project.
-All authors contributed to the manuscript revisions.
+All authors contributed to manuscript revisions.
 

### 2022-06-22 article.tex
Add discussion. Revise conclusion. More edits.

@@
 Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution.
-This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and neurosurgical use \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.
+This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.
 
-Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify controlled flow changes in well-defined channels.
+Due to its widespread adoption, LSCI instrument design and development is an active area of research with microfluidic studies commonly used to quantify controlled flow changes in well-defined channels.
 Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}.
 More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}.
-A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged.
-For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}.
-This speed is converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.
+A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI.
+For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}.
+This speed can be converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.
 
-Syringe pumps are the most widely used flow control system in microfluidic studies and are commonly believed to provide a highly-controlled flow output.
-\textcolor{red}{A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps}; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}.
+Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output.
+A survey of 21 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments.
+The devices were from a variety of manufacturers and featured various syringe sizes and materials.
 However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}.
@@
 
-A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor altogether and can provide very stable flow rates \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
-This method involves using compressed air and a pressure regulator to pressurize a reservoir holding the solution, and then applying a controlled pressure to push solution through the microfluidic device at constant flow rates.
-A feedback loop, with an in-line flow measurement device, can be used to adjust the pressure level to achieve a desired flow rate, which allows the user to request a desired flow rate rather than a pressure level.
+A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor and lead screw in order to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
+These systems use compressed air to push liquid from a pressure-regulated reservoir through the microfluidic device at constant flow rates.
+Integration with an inline flow measurement device allows for feedback loop control and the programming of specific flow rates rather than pressure levels.
 
 One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}.
-Standard LSCI systems use a single camera exposure time, limiting flow sensitivity to a small range.
-Additionally, several instrumentation factors, namely, illumination variations and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making.
+Standard LSCI systems use a single camera exposure time, limiting sensitivity to a small range of flows.
+Additionally, instrumentation factors such as illumination variation and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making.
 An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}.
@@
 \label{sect:methods_phantom}
-The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) per gram of PDMS added to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
+The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
 The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom.
@@
 The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel.
-Inlet and outlet ports were attached using 23G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
-Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was used to connect to the blunt tip ports as inlet and outlet tubing.
-The inlet tubing was connected to the flow sensor and the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.).
-The outlet tubing drained into a vial, with the tubing end submerged in solution.
-A photograph of the finished phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS and the glass slide seals the surface.
+Inlet and outlet ports were attached using 23 G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
+Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing.
+The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.).
+The outlet tubing drained into a vial, with the tubing end fully submerged in liquid.
+A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.
 
@@
     \caption {
-        (a) Photograph of the machined aluminum mold with a 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, extrusion used to cast the PDMS during fabrication of the microfluidic flow phantom.
+        (a) Photograph of the machined aluminum mold with a 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm extrusion used to cast the PDMS during fabrication of the microfluidic flow phantom.
 (b) Photograph of the finished microfluidic flow phantom, showing PDMS bonded to a glass slide, with inlet and outlet ports secured using epoxy.
@@
 Based on Ref.
-\cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit = 0.5 is approximately 20 cm$^{-1}$.
-By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of by 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$.
-However, we note that the anisotropy of the microspheres in our solution is different that that of whole blood ($g = 0.92$ compared to $g = 0.98$).
-The blood-mimicking solution was preferred over whole blood for several reasons, namely: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water flow.
+\cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$.
+By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$.
+However, we note that the anisotropy of the microspheres in our solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$).
+The blood-mimicking solution was preferred over whole blood for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water.
 Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid.
 The solution of microspheres was freshly mixed before each experiment to reduce aggregation of particles in the dilution.
-Once mixed, the solution was sonicated (10 minutes) to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.
+Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.
 
@@
 To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel.
-A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a.
-The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) was used to record the absolute flow rate.
+A thermal mass flow sensor (FLU-L, 0.03 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a.
+The sensor output was digitized and relayed to a computer via an accompanying hub (Flowboard, FLB, Fluigent, Inc.) where the MAESFLO software (Fluigent, Inc.) was used to monitor and record the absolute flow rate.
 All flow sensor measurements were downsampled from 10 Hz to 2 Hz using interpolation to match the timing of the optical measurements.
 
-The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system_lsci}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution as described in Section \ref{sect:methods_phantom}.
-The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output.
-It should be noted that a 3 mL syringe was also tested, however its performance was significantly worse than the 10 mL syringe and, in some cases, could not resolve the desired flow profiles.
+The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}.
+The syringe pump was programmed to run a predefined flow profile, using the inner diameter of the syringe (14.5 mm) to ensure correct flow rate output.
+It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.
 
-The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system_lsci}c.
+The pressure-regulated flow system used a pressure controller (MFCS-EZ with 69 mbar channel, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c.
 This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution.
 Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure.
-The pressure control system used built-in software (MAESFLO) to provide feedback from the inline flow sensor to regulate the pressure to achieve the desired flow rate.
+The MAESFLO control software used feedback from the inline flow sensor to regulate the air pressure to achieve the desired flow rate.
 
@@
 
-Finally, the uncertainty in measurement bias, was defined as:
+Finally, the uncertainty in measurement bias, an estimate of flow accuracy, was defined as:
 %
@@
 A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging.
-\textcolor{red}{Is there a filter?
-Specifics of f-number and speckle size?} The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++.
+The aperture of the lower lens was set to
+$f$/11 in order to properly sample the speckle pattern \cite{Kirkpatrick:2008ke} while the upper lens was left at its maximum size of $f$/1.8.
+A longpass red filter (600 nm, R-60, Edmund Optics, Inc.) was placed between the two lenses to filter stray background light.
+The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++.
 The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm.
-The camera exposure time was set to 0.5 ms and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps).
-\textcolor{red}{Explanation for 0.5 ms exposure time?}
+The camera exposure time was set to 0.5 ms
+and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps).
 
@@
 Raw intensity images were converted to speckle contrast images using Eq.
-\ref{eq:sc}, where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) in a sliding 7$\times$7-pixel window centered at every pixel.
+\ref{eq:sc}, where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) in a sliding 7$\times$7-pixel window centered at every pixel of the raw image.
 %
@@
 By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time.
-\textcolor{red}{Unclear if there was additional averaging performed by the Speckle Software (i.e.
-frames/sequence=15?
-Was the saved SC data already averaged?)} During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel.
+During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel.
 This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}.
@@
 In order to compare the LSCI measurements with the flow sensor, the relative flow for each technique was calculated using the average value of the first step (2.4 mm/s) as the baseline.
-The initial rise of the first flow step was also used to synchronize the timing of the two datasets.
+Because the flow sensor software used a separate clock than the LSCI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step.
 
@@
 A schematic of the MESI setup is shown in Fig.~\ref{fig:system_mesi}.
-MESI was performed \cite{Parthasarathy:2008el} using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.).
+MESI was performed using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.).
 The operating current on the laser diode controller (LDC205C, Thorlabs, Inc.) was fixed at 380 mA (300 mW) and the target temperature set to 25 $^\circ$C on the temperature controller (TED200C, Thorlabs, Inc.).
 The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance.
-Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled \textcolor{red}{(Which lens?)} into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam.
+Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled into a single-mode fiber optic patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam.
 The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the microfluidic.
@@
 A pair of consumer camera lenses were used to image the scattered light (AF Nikkor 50 mm $f$/1.8D + AF Micro-Nikkor 105 mm $f$/2.8D, Nikon Corp.) with 2.1$\times$ magnification through a bandpass filter (785$\pm$31 nm, 87-773, Edmund Optics Inc.) to a CMOS camera (acA1920-155um, 1920 $\times$ 1200 pixels, Basler AG).
+The aperture of the lower lens was set to $f$/5.6 while the upper lens was left at its maximum size of $f$/2.8.
 Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm.
@@
 The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
-The entire acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.
+The entire acquisition was controlled using custom software written in C++ integrated with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.
 
@@
     \caption {
-        System schematic for microfluidic flow assessment of MESI and LSCI with the pressure-regulated flow system.
+        System schematic for microfluidic flow assessment of MESI and LSCI measurements using only the pressure-regulated flow system.
     }
@@
 Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}.
-Because the flow sensor software used a separate clock than the MESI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step.
+The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets.
 The experiment was repeated a total of four times across two days.
 
-The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described in Section \ref{sect:methods_lsci}.
+The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described previously in Section \ref{sect:methods_lsci}.
 The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
@@
 All fitting was performed with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in MATLAB (R2021a, MathWorks, Inc.).
-The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).
+The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation, smoothed temporally with a central moving average filter ($k=5$), and inverted to obtain $ICT$.
 
@@
 The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor is shown in Fig.~\ref{fig:SvP-FS}.
-These plots demonstrate that the pressure-regulated system outperforms the syringe pump by accurately and steadily matching the programmed flow speeds across both experiments.
-While both flow systems responded quickly to the desired flow changes during the large step size experiment (Fig.~\ref{fig:SvP-FS}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated system.
+These plots demonstrate that the pressure-regulated flow system outperforms the syringe pump by accurately and steadily matching the programmed flow speeds across both experiments.
+While both flow systems responded quickly to the desired flow changes during the large step size experiment (Fig.~\ref{fig:SvP-FS}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated flow system.
 Furthermore, the small step size experiment (Fig.~\ref{fig:SvP-FS}b) demonstrated that the syringe pump system could not reliably reproduce the finer flow changes as evidenced by the loss of the stair-stepped flow pattern.
@@
 
-Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiment.
-These results confirm the observations from Fig.~\ref{fig:SvP-FS} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds.
+Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiments.
+These results quantify the observations from Fig.~\ref{fig:SvP-FS} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds.
 The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}.
 These results provide evidence of the superiority of the pressure-regulated flow system, particularly when attempting to produce small flow changes.
-With the syringe pump system, it would be impossible to reliably separate changes in relative flow of 20\% from flow system noise at the 2.4 mm/s flow speed.
+With the syringe pump system, it would be impossible to reliably separate 20\% changes in relative flow from flow system noise at the 2.4 mm/s flow speed.
 This magnitude of uncertainty in flow generation would make it difficult to assess an optical system's ability to detect small changes in flow.
@@
 
-The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and LSCI is shown in Fig.~\ref{fig:SvP-FS_LSCI}.
-The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step.
+The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and single-exposure LSCI is shown in Fig.~\ref{fig:SvP-FS_LSCI}.
+The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step to permit comparison.
 The relative flow changes measured by LSCI closely track those of the flow sensor and corroborate the accuracy and stability issues seen with the syringe pump system.
-These results also demonstrate that LSCI is capable of detecting similar changes in flow as the commercial flow sensor for relative flow changes up to double the baseline \textcolor{red}{(awkward wording)}.
+These results demonstrate that LSCI is capable of detecting similar changes as the commercial flow sensor when measuring relative flow changes up to double the baseline.
 
@@
 The concordance correlation coefficients ($\rho_c$), a metric designed to evaluate reproducibility \cite{Lin.1989}, were 0.994 and 0.908, respectively.
-These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI increasingly outperforms LSCI across large changes in relative flow.
+These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI outperforms LSCI across large changes in relative flow.
+\textcolor{red}{Address apparent differences in performance for LSCI between Figs.
+\ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci}?
+The flow at the 5 mm/s step is $\sim$1.93$\times$ the flow at the 2.5 mm/s step in Fig.
+\ref{fig:flow_mesi_lsci}.
+Not quite the near-perfect agreement we see in Fig.
+\ref{fig:SvP-FS_LSCI}b.}
 
@@
 The absolute error for MESI was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it increased to almost 9\%.
-In contrast, the LSCI error was over 8\% for all flow speeds, increasing to over 17\% for flow speeds greater than 4 mm/s.
+In contrast, the LSCI error was over 8.2\% for all flow speeds, increasing to over 17\% for flow speeds greater than 4 mm/s.
+Aggregated across all flow speeds, the average absolute error for MESI was 4.6 $\pm$ 2.6\% and LSCI was 15.7 $\pm$ 4.6\%.
+\textcolor{red}{Does it make sense reporting the numbers this way?}
 
@@
 
-\blindtext
+Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps.
+This study corroborates previous work \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies.
+Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials.
+Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the flow measurements, making it more difficult to properly characterize a system.
+For example, the flow profiles in Fig.
+\ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump.
+These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig.
+\ref{fig:SvP-FS_LSCI}a.
+Such instability would increase the uncertainty in the true performance of any instrument being evaluated.
+The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.
+
+\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?}} Compare results to manufacturer's spec.
+How to explain the syringe pump results being so far off?
+Accuracy +/- 0.5\%, Reproducibility +/- 0.05\%.
+The accuracy ($u_{bias}$) of the syringe pump is the primary source of uncertainty.
+Possibly move part of results text here instead?
+
+The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp,Sullender.2022}.
+The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements.
+This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline.
+As seen in Fig.
+\ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI.
+\textcolor{red}{Compare to previous measurements by Shams?
+Can we suggest that the slightly lower errors could be caused by using syringe pump systems?} While MESI exhibited slightly more variability during individual flow profile steps (Fig.
+\ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to estimate $\tau_c$.
+This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s.
+\textcolor{red}{Can we actually claim this?
+If yes, then what exactly is happening?
+Is it just changes in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located.
+Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.
+
+The linearity of the results seen with both MESI and LSCI suggest that a calibration to absolute flow speeds might be feasible.
+However, any such calibration would be highly dependent upon experimental parameters, including the sample geometry (i.e.
+channel size), scatterer concentration, illumination configuration, and exposure time selection \textcolor{red}{(Any other major ones?)}.
+Changes to any of these parameters would produce different $ICT$ values, which would affect the correlation with the flow sensor and invalidate the calibration.
+It also remains to be seen whether calibrations performed in controlled microfluidic environments can reliably be translated to \textit{in vivo} measurements in animal or human subjects.
+\textcolor{red}{Should we elaborate further and give examples?}
+
+While the pressure-regulated flow system outperformed the syringe pump during testing, it has two major disadvantages: increased cost and difficulty of use.
+For the models used in this study, the pressure-regulated flow system was $\sim$3.5$\times$ more expensive than the syringe pump.
+Although there is variability in pricing for both types of systems depending on the vendor and specific features, pressure-regulated flow systems are consistently the more expensive.
+They are also considerably more difficult to use and maintain than a syringe pump, which simply requires filling a syringe with solution, securing it to the pump, and specifying the desired flow rate.
+The setup for a syringe pump can be performed quickly with minimal room for error.
+In contrast, the pressure-regulated flow system requires an extensive setup process and much greater care must be taken in order to achieve the stated performance of the device.
+For example, in order to maximize stability, tubing lengths must be selected to achieve a certain level of resistance in the system such that the desired flow range (0 -- 60.9 $\mu$L/min) spans the available range of the pressure controller (0 -- 69 mbar).
+Furthermore, since fluidic fittings are required for connecting all system components, diagnosing instabilities caused by air leakage from an improperly secured fitting can become a difficult endeavor.
+The system also requires a calibration procedure before any flow program can be executed.
+While this helps ensure a high level of performance, it is an additional step during an already lengthy setup process.
+Overall, the pressure-regulated flow system was more tedious and had much greater potential for error.
+However, in order to accurately test instrument sensitivity to small flow changes, the pressure-regulated flow system was the only option with the necessary stability and reliability required to produce such flow changes.
 
@@
 
-This paper demonstrates that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of optical imaging systems using microfluidics.
+This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies.
+While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems.
+We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics.
 We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds.
-Furthermore, we demonstrate that MESI can be used to detect changes in relative flow as small as 5\%.
-Given the large uncertainties associated with syringe pump systems, it would be impossible to determine that such a measurement arose from an actual flow change rather than random or systematic error.
-These results indicate that it is necessary to use a pressure-regulated flow system in order to properly assess the performance of a MESI system or when characterizing hardware changes to such a system.
+We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI.
+Using a commercial flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively.
+Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than random or systematic error.
+Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.
 
@@
 \subsection*{Disclosures}
-A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.
+A.K.D. holds equity in and serves on the board of directors of Dynamic Light, Inc. The authors declare no other conflicts of interest.
 
@@
 \vspace{1ex}
-\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering.
-He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.
-He is the author of more than 50 journal papers and has written three book chapters.
-His current research interests include optical interconnects, holography, and optoelectronic systems.
-He is a member of SPIE.
+\vspace{2ex}\noindent\textbf{Colin T.
+Sullender} is a postdoctoral fellow at the University of Texas at Austin.
+He received his B.S.
+in Bioengineering from the University of Washington and his M.S.E and Ph.D.
+in Biomedical Engineering from the University of Texas at Austin.
+His current research focuses on developing laser speckle contrast imaging techniques for studying neurovascular hemodynamics.
 
-\vspace{1ex}
-\noindent Biographies and photographs of the other authors are not available.
+\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin. He received his B.Eng., M.S.E., and Ph.D. in Electrical Engineering from McGill University.
+
+\vspace{2ex}\noindent\textbf{Lisa M.
+Richards} was a postdoctoral fellow at the University of Texas at Austin when this research was conducted.
+She received her B.S.E in Biomedical Engineering from Duke University and her M.S.E.
+and Ph.D.
+in Biomedical Engineering from the University of Texas at Austin.
+
+\vspace{2ex}\noindent\textbf{Andrew K.
+Dunn} is the Edward S.
+Hyman Endowed Chair in Engineering in the Department of Biomedical Engineering and the Director of the Center for Emerging Imaging Technologies (CEIT) at the University of Texas at Austin.
+He pioneered the use of laser speckle contrast imaging to measure blood flow in the brain and has more than 50 publications on the subject.
+His research focuses on the development of novel optical imaging techniques for studying the brain.
 

### 2022-06-27 article.tex
Rewrite introduction

@@
 % Include a list of up to six keywords after the abstract
-\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, flow measurement, microfluidic, flow system}
+\keywords{laser speckle contrast imaging, multi-exposure speckle imaging, flow measurement, microfluidic, flow system}
 
@@
 
-Monitoring cerebral blood flow (CBF) is essential during neurosurgery as it provides surgeons with the critical information needed to guide life-saving interventions and is a valuable tool in mitigating post-operative complications \cite{Kirkness.2005}.
-As such, a clinical system that provides continuous CBF monitoring is highly desired.
-Laser speckle contrast imaging (LSCI) is a noninvasive, label-free, optical imaging technique based on coherent dynamic light scattering that has been widely implemented for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}.
+Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}.
 Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution.
-This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.
+This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}.
+Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}.
+The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors.
+These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.
 
-Due to its widespread adoption, LSCI instrument design and development is an active area of research with microfluidic studies commonly used to quantify controlled flow changes in well-defined channels.
-Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}.
-More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}.
-A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI.
+Due to its popularity, LSCI (and MESI) instrument development is an active area of research with microfluidic studies commonly used to characterize performance in controlled flow environments.
+Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) substrate \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Arias-Cruz.2019}, or clear plastic tubing \cite{Miao:2014}.
+More complex microfluidic networks have also been fabricated in glass, plastic, or epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}.
+A scattering solution \cite{Parthasarathy:2008el,Arias-Cruz.2019} or whole blood \cite{Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI.
 For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}.
-This speed can be converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.
+This speed can be converted to a volumetric flow rate using the cross-sectional area of the flow channel, which is then used to program the flow control system.
 
 Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output.
-A survey of 21 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments.
+A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments.
 The devices were from a variety of manufacturers and featured various syringe sizes and materials.
+Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed.
+A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate.
 However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}.
-Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}.
-The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.
+Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}.
+The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump flow control system.
 
-A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor and lead screw in order to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
-These systems use compressed air to push liquid from a pressure-regulated reservoir through the microfluidic device at constant flow rates.
-Integration with an inline flow measurement device allows for feedback loop control and the programming of specific flow rates rather than pressure levels.
+Pressure-driven flow regulation systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
+These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate.
+In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device.
+Thermal mass flow sensors are commonly used to measure the low flow rates found in microfluidics.
+These sensors use heating and temperature-sensing elements to detect the magnitude and direction of flow and are factory-calibrated to measure absolute flow rates for various fluids.
+Integration of the flow sensor with a feedback loop allows for the programming of specific flow rates rather than pressure levels.
 
-One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}.
-Standard LSCI systems use a single camera exposure time, limiting sensitivity to a small range of flows.
-Additionally, instrumentation factors such as illumination variation and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making.
-An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}.
-MESI has been shown to be reliable for chronic imaging and to have high correlation with \textit{in vivo} absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons.
-By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.
-
-In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regulated flow system.
-By understanding the associated uncertainty with each system, we can provide insight on the experimental design for a microfluidic study that aims to assess the hardware performance of an optical system, without fear that performance can be compromised due to flow-related noise.
-Quantifying this error allows us to accurately determine the true sensitivity to relative flow changes of a MESI system.
-\textcolor{red}{Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%.} The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.
+In this paper, we address two primary objectives.
+First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system.
+By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors.
+Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds.
+Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI.
+Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation.
+The results of this study indicate that characterizing optical techniques with microfluidic studies requires highly-accurate flow control.
 

### 2022-06-27 article.tex
Remove unused BibTeX entries

@@
 The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors.
-These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.
+These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020,Sullender.2022} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.
 
@@
 
-The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp,Sullender.2022}.
+The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}.
 The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements.

### 2022-06-28 article.tex
Rewrite (structured) abstract

@@
 \usepackage{xcolor}
+
+% Structured abstract section formatting
+\newcommand{\abstractsection}[1]{
+  \par\addvspace{.5\baselineskip}
+  \noindent\textbf{#1: }\ignorespaces
+}
 
@@
 \begin{abstract}
-Laser speckle contrast imaging (LSCI) is a label-free optical imaging technique that can provide quantitative blood flow data, which can be beneficial during specific neurosurgeries.
-Microfluidic phantoms are commonly used in the development of LSCI systems as they allow for system characterization and ease of hardware optimization.
-In this paper, we demonstrate that pressure-driven flow systems can be used to accurately and precisely control flow changes as small as 2\%, in comparison to the commonly used syringe pump systems that have difficulty resolving changes in flow of 5\%.
-Furthermore, we demonstrate that a multi-exposure speckle imaging (MESI) system is sensitive to small changes in flow and can accurately and repeatably quantify changes in flow as small as 2\%.
-These results indicate that for the characterization and development of LSCI, or MESI, systems, and to mitigate any concerns with the uncertainty in the actual flow-profile and not the hardware itself, pressure-based flow systems should be used with microfluidic channels.
+
+\abstractsection{Significance}
+Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) and multi-exposure speckle imaging (MESI) instruments.
+The selection of the flow control system is critical for the reliable generation of flow during accuracy and sensitivity testing.
+The majority of recent LSCI studies using microfluidics used syringe pump flow control systems.
+
+\abstractsection{Aim}
+We quantified the uncertainty in flow generation for a syringe pump and a pressure-regulated flow system.
+We then assessed the performance of both LSCI and MESI using the pressure-regulated flow system across a range of physiologically-relevant flow speeds.
+
+\abstractsection{Approach}
+The syringe pump and pressure-regulated flow systems were evaluated during stepped flow profile experiments in a microfluidic device using an inline flow sensor.
+The uncertainty associated with each flow system was calculated and used to determine the reliability for LSCI instrument testing.
+The pressure-regulated flow system was then used to characterize the relative performance of LSCI and MESI during stepped flow profile experiments while using the inline flow sensor as reference.
+
+\abstractsection{Results}
+The pressure-regulated flow system produced much more stable and reproducible flow outputs compared to the syringe pump.
+The expanded uncertainty for the syringe pump was 8--20$\times$ higher than that of the pressure-regulated flow system across the tested flow speeds \textcolor{red}{(Should we use exact numbers here?
+If so, which flow speeds?)}.
+Using the pressure-regulated flow system, MESI outperformed single-exposure LSCI at all flow speeds and closely mirrored the flow sensor measurements, with average errors of 4.6\% and 15.7\%, respectively \textcolor{red}{(Include $\pm$ std too?)}.
+
+\abstractsection{Conclusions}
+Pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of flow measurement techniques with microfluidic studies.
+MESI offers more accurate relative flow measurements than traditional LSCI across a wide range of flow speeds.
+
 \end{abstract}
@@
 Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation.
-The results of this study indicate that characterizing optical techniques with microfluidic studies requires highly-accurate flow control.
+The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing optical imaging techniques with microfluidic studies.
 
@@
 
-\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?}} Compare results to manufacturer's spec.
+\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?} Compare results to manufacturer's spec.
 How to explain the syringe pump results being so far off?
@@
 The accuracy ($u_{bias}$) of the syringe pump is the primary source of uncertainty.
-Possibly move part of results text here instead?
+Possibly move part of results text here instead?}
 
@@
 We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI.
-Using a commercial flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively.
+Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively.
 Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than random or systematic error.

### 2022-06-29 article.tex
Revisions

@@
 \abstractsection{Significance}
-Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) and multi-exposure speckle imaging (MESI) instruments.
-The selection of the flow control system is critical for the reliable generation of flow during accuracy and sensitivity testing.
-The majority of recent LSCI studies using microfluidics used syringe pump flow control systems.
+Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) instruments.
+The selection of the flow control system is critical for the reliable generation of flow during testing.
+The majority of recent LSCI studies using microfluidics used syringe pumps for flow control.
 
@@
 We quantified the uncertainty in flow generation for a syringe pump and a pressure-regulated flow system.
-We then assessed the performance of both LSCI and MESI using the pressure-regulated flow system across a range of physiologically-relevant flow speeds.
+We then assessed the performance of both LSCI and multi-exposure speckle imaging (MESI) using the pressure-regulated flow system across a range of flow speeds.
 
@@
 The syringe pump and pressure-regulated flow systems were evaluated during stepped flow profile experiments in a microfluidic device using an inline flow sensor.
-The uncertainty associated with each flow system was calculated and used to determine the reliability for LSCI instrument testing.
+The uncertainty associated with each flow system was calculated and used to determine the reliability for instrument testing.
 The pressure-regulated flow system was then used to characterize the relative performance of LSCI and MESI during stepped flow profile experiments while using the inline flow sensor as reference.
@@
 % Include a list of up to six keywords after the abstract
-\keywords{laser speckle contrast imaging, multi-exposure speckle imaging, flow measurement, microfluidic, flow system}
+\keywords{laser speckle contrast imaging, multi-exposure speckle imaging, dynamic light scattering, flow measurement, microfluidic, flow system}
 
@@
 Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution.
-This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}.
+This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}.
 Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}.
@@
 
-Due to its popularity, LSCI (and MESI) instrument development is an active area of research with microfluidic studies commonly used to characterize performance in controlled flow environments.
+Due to its popularity, LSCI instrument development is an active area of research with microfluidic studies commonly used to characterize performance in controlled flow environments.
 Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) substrate \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Arias-Cruz.2019}, or clear plastic tubing \cite{Miao:2014}.
@@
 Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}.
-The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump flow control system.
+The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system.
 
-Pressure-driven flow regulation systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
+Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
 These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate.
@@
 Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation.
-The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing optical imaging techniques with microfluidic studies.
+The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing flow measurement techniques with microfluidic studies.
 
@@
 \label{sect:methods_phantom}
-The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
+The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
 The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom.
@@
 The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring.
-The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold.
+The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold.
 The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel.
-Inlet and outlet ports were attached using 23 G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
+Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
 Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing.
@@
 \cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$.
-By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$.
-However, we note that the anisotropy of the microspheres in our solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$).
-The blood-mimicking solution was preferred over whole blood for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water.
+By using a 7\% by volume mixture of the microsphere solution and UFDI water (e.g.
+10 mL of blood mimicking solution = 0.7 mL of the 5100A solution + 9.3 mL UFDI water) we were able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$.
+However, we note that the anisotropy of the microsphere solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$).
+The blood-mimicking solution was preferred for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water.
 Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid.
-The solution of microspheres was freshly mixed before each experiment to reduce aggregation of particles in the dilution.
+The solution of microspheres was freshly mixed before each experiment to reduce particle aggregation.
 Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.
@@
 The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}.
-The syringe pump was programmed to run a predefined flow profile, using the inner diameter of the syringe (14.5 mm) to ensure correct flow rate output.
+The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate.
 It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.
 
-The pressure-regulated flow system used a pressure controller (MFCS-EZ with 69 mbar channel, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c.
+The pressure-regulated flow system used a pressure controller (MFCS-EZ, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c.
 This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution.
@@
     \caption {
-        (a) LSCI system schematic for microfluidic flow assessment.
+        (a) LSCI system schematic for microfluidic flow assessment (L = Lens, F = Filter).
 A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements.
@@
     \caption {
-        System schematic for microfluidic flow assessment of MESI and LSCI measurements using only the pressure-regulated flow system.
+        System schematic for microfluidic flow assessment of MESI and LSCI measurements using only the pressure-regulated flow system (A = Aperture, M = Mirror, L = Lens, F = Filter).
     }
@@
 MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps).
-Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}.
+Single-exposure (0.5 ms) LSCI frames were extracted from the MESI dataset \textit{post hoc}.
 The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets.
@@
 In contrast, the LSCI error was over 8.2\% for all flow speeds, increasing to over 17\% for flow speeds greater than 4 mm/s.
-Aggregated across all flow speeds, the average absolute error for MESI was 4.6 $\pm$ 2.6\% and LSCI was 15.7 $\pm$ 4.6\%.
-\textcolor{red}{Does it make sense reporting the numbers this way?}
+Aggregated across all tested flow speeds, the average absolute error for MESI was 4.6 $\pm$ 2.6\% and LSCI was 15.7 $\pm$ 4.6\%.
 
@@
 Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials.
-Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the flow measurements, making it more difficult to properly characterize a system.
+Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the measurements, making it more difficult to properly characterize a system.
 For example, the flow profiles in Fig.
@@
 \textcolor{red}{Compare to previous measurements by Shams?
-Can we suggest that the slightly lower errors could be caused by using syringe pump systems?} While MESI exhibited slightly more variability during individual flow profile steps (Fig.
-\ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to estimate $\tau_c$.
+Can we suggest that the reduced error was caused by the syringe pump?} While MESI exhibited slightly more variability during individual flow profile steps (Fig.
+\ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to calculate $\tau_c$.
 This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s.
@@
 If yes, then what exactly is happening?
-Is it just changes in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located.
+Is it just numerical changes in the fitting caused by increases in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located.
 Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.
@@
 Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively.
-Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than random or systematic error.
+Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than systematic error.
 Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.

### 2022-06-29 article.tex
Update microfluidic syringe pump vs. pressure citations

@@
 A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate.
-However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}.
+However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Li:2014ca,Zeng.2014}.
 Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}.
@@
 
-Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}.
-These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate.
+Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Zhou:2011ey,Li:2014ca,Zeng.2020}.
+These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate \cite{Zeng.2020}.
 In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device.

### 2022-07-06 article.tex
Edits from Andy and Adam

@@
 \usepackage{graphicx}
-\usepackage{setspace}
 \usepackage{tocloft}
@@
 \usepackage{booktabs}
-\usepackage{blindtext}
-\usepackage{xcolor}
 
@@
 \abstractsection{Significance}
-Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) instruments.
+Microfluidic flow phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) instruments.
 The selection of the flow control system is critical for the reliable generation of flow during testing.
@@
 The pressure-regulated flow system produced much more stable and reproducible flow outputs compared to the syringe pump.
-The expanded uncertainty for the syringe pump was 8--20$\times$ higher than that of the pressure-regulated flow system across the tested flow speeds \textcolor{red}{(Should we use exact numbers here?
-If so, which flow speeds?)}.
-Using the pressure-regulated flow system, MESI outperformed single-exposure LSCI at all flow speeds and closely mirrored the flow sensor measurements, with average errors of 4.6\% and 15.7\%, respectively \textcolor{red}{(Include $\pm$ std too?)}.
+The expanded uncertainty for the syringe pump was 8--20$\times$ higher than that of the pressure-regulated flow system across the tested flow speeds.
+Using the pressure-regulated flow system, MESI outperformed single-exposure LSCI at all flow speeds and closely mirrored the flow sensor measurements, with average errors of 4.6 $\pm$ 2.6\% and 15.7 $\pm$ 4.6\%, respectively.
 
@@
 Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}.
-The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system.
+The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system, both of which are necessary for LSCI characterization measurements.
 
@@
 In this paper, we address two primary objectives.
-First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system.
+First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system in microfluidic flow phantoms commonly used with optical blood flow imaging instruments.
 By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors.
@@
 Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation.
-The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing flow measurement techniques with microfluidic studies.
+The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing laser speckle techniques with microfluidic studies.
 
@@
 \label{sect:methods_phantom}
-The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
+
+The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties at near infrared wavelengths ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
 The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom.
@@
 Based on Ref.
-\cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$.
+\citen{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$.
 By using a 7\% by volume mixture of the microsphere solution and UFDI water (e.g.
@@
 \subsection{Microfluidic Flow System Instrumentation}
+\label{sect:methods_flow_system}
 
@@
 \subsection{LSCI Instrumentation}
+\label{sect:methods_lsci_system}
 
@@
 A longpass red filter (600 nm, R-60, Edmund Optics, Inc.) was placed between the two lenses to filter stray background light.
-The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++.
+The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software.
 The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm.
@@
 \subsection{LSCI Flow Measurements}
-\label{sect:methods_lsci}
+\label{sect:methods_lsci_measure}
 
@@
 
-By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time.
 During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel.
@@
 \subsection{MESI Instrumentation}
+\label{sect:methods_mesi_system}
 
@@
 \subsection{MESI and LSCI Performance}
+\label{sect:methods_mesi_lsci_measure}
 
-A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI.
+A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI using the same optical hardware.
 The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments.
@@
 
-The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described previously in Section \ref{sect:methods_lsci}.
+The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described previously in Section \ref{sect:methods_lsci_measure}.
 The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
@@
 \subsection{Microfluidic Flow System Assessment}
+\label{sect:results_flow_assess}
 
@@
 \subsection{LSCI Flow Measurements}
+\label{sect:results_lsci_measure}
 
-The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and single-exposure LSCI is shown in Fig.~\ref{fig:SvP-FS_LSCI}.
+The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and single-exposure LSCI using the system described in Section \ref{sect:methods_lsci_system} is shown in Fig.~\ref{fig:SvP-FS_LSCI}.
 The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step to permit comparison.
@@
 \subsection{MESI and LSCI Performance}
+\label{sect:results_mesi_lsci_measure}
 
 The flow measurement performance assessment using the pressure-regulated flow system is shown in Fig.~\ref{fig:flow_mesi_lsci}.
-The relative flow measured by MESI and LSCI are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a.
+The relative flow measured by MESI and LSCI using the system described in Section \ref{sect:methods_mesi_system} are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a.
 All relative flows were calculated using the average of the first flow step (1 mm/s) as the baseline.
@@
 Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps.
-This study corroborates previous work \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies.
+This study corroborates previous work \cite{Li:2014ca,Zhou:2011ey,Zeng.2020} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies (Fig.
+\ref{fig:SvP-FS_LSCI}).
+Furthermore, the close agreement between the LSCI and flow sensor demonstrates that these flow anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations.
 Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials.
@@
 However, any such calibration would be highly dependent upon experimental parameters, including the sample geometry (i.e.
-channel size), scatterer concentration, illumination configuration, and exposure time selection \textcolor{red}{(Any other major ones?)}.
+channel size), scatterer concentration, illumination configuration, and exposure time selection.
 Changes to any of these parameters would produce different $ICT$ values, which would affect the correlation with the flow sensor and invalidate the calibration.
-It also remains to be seen whether calibrations performed in controlled microfluidic environments can reliably be translated to \textit{in vivo} measurements in animal or human subjects.
-\textcolor{red}{Should we elaborate further and give examples?}
+It also remains to be seen whether calibrations performed in controlled microfluidic environments can reliably be translated to animal or human subjects since \textit{in vivo} measurements sample a range of different vessels \cite{Davis:2016ik,Jafari.2020}.
 

### 2022-07-08 article.tex
Add discussion of uncertainty relative to device spec

@@
 
-The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}.
+The syringe pump system (74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}.
 The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate.
-It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.
+It should be noted that a 3 mL syringe was also evaluated, however its performance was worse than the 10 mL syringe and could not hold sufficient volume for all trials without being refilled.
 
-The pressure-regulated flow system used a pressure controller (MFCS-EZ, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c.
+The pressure-regulated flow system used a pressure controller (MFCS-EZ with 69 mbar channel, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c.
 This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution.
@@
 This limitation is visually represented in Fig.~\ref{fig:SvP-FS}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes.
-Using the pressure-regulated flow system, experiments could be designed with relative flow changes of only 1.5\% while remaining confident that the resulting optical system measurements were not caused by flow system noise.
+Using the pressure-regulated flow system, experiments could be designed with relative flow changes of only 1.25\% while remaining confident that the resulting optical system measurements were not caused by flow system noise.
 This level of certainty would also permit assessing improvements to optical system performance at this scale.
@@
 These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI outperforms LSCI across large changes in relative flow.
-\textcolor{red}{Address apparent differences in performance for LSCI between Figs.
-\ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci}?
-The flow at the 5 mm/s step is $\sim$1.93$\times$ the flow at the 2.5 mm/s step in Fig.
-\ref{fig:flow_mesi_lsci}.
-Not quite the near-perfect agreement we see in Fig.
-\ref{fig:SvP-FS_LSCI}b.}
+It should be noted that the apparent disparity in LSCI performance between Figs.
+\ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci} is primarily the result of different flow steps being used as the baseline in each set of experiments.
+While not an exact comparison, the LSCI measured flow at the 5 mm/s step is 1.94$\times$ the flow at the 2.5 mm/s step in Fig.
+\ref{fig:flow_mesi_lsci}, approximately mirroring the 2$\times$ change seen between the 2.4 and 4.8 mm/s steps in Fig.
+\ref{fig:SvP-FS_LSCI}b.
 
@@
 \ref{fig:SvP-FS_LSCI}).
-Furthermore, the close agreement between the LSCI and flow sensor demonstrates that these flow anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations.
+Furthermore, the close agreement between LSCI and the flow sensor demonstrates that these anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations.
 Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials.
@@
 
-\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?} Compare results to manufacturer's spec.
-How to explain the syringe pump results being so far off?
-Accuracy +/- 0.5\%, Reproducibility +/- 0.05\%.
-The accuracy ($u_{bias}$) of the syringe pump is the primary source of uncertainty.
-Possibly move part of results text here instead?}
+The measured noise levels quantified by $u_\textnormal{repeat}$ follow the specifications published by the manufacturers of both flow control systems.
+This indicates that the stability results shown are typical and representative of actual performance differences.
+The $u_\textnormal{repeat}$ for the syringe pump across all flow steps (up to 1.86\%) was within the manufacturer's tolerances, which stated that instantaneous flow should be $\pm$2\% from the mean value.
+The $u_\textnormal{repeat}$ for the pressure-regulated flow system (up to 0.55\%) slightly exceeded the manufacturer's specifications, which indicated that the best stability achievable with this system configuration was $\pm$0.5\% from the mean value.
+Much larger differences arose from issues with reproducibility and accuracy, with the $u_\textnormal{reproduce}$ and $u_\textnormal{bias}$ of the syringe pump measuring several orders of magnitude higher than those of the pressure-regulated flow system.
+The syringe pump greatly exceeded the manufacturer's tolerances for both reproducibility ($\pm$0.05\%) and accuracy ($\pm$0.5\%).
+Corresponding specifications were not available for the pressure-regulated flow system.
+While it is possible that using a glass syringe \cite{Zhou:2011ey} or sending the device for manufacturer recalibration could improve performance on the syringe pump, it is unlikely to achieve the stability and reliability seen with the pressure-regulated flow system.
 
@@
 \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI.
-\textcolor{red}{Compare to previous measurements by Shams?
-Can we suggest that the reduced error was caused by the syringe pump?} While MESI exhibited slightly more variability during individual flow profile steps (Fig.
-\ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to calculate $\tau_c$.
-This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s.
-\textcolor{red}{Can we actually claim this?
-If yes, then what exactly is happening?
-Is it just numerical changes in the fitting caused by increases in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located.
+While MESI exhibited slightly more variability during individual flow profile steps (Fig.
+\ref{fig:flow_mesi_lsci}a), this was likely caused by the fitting process required to calculate $\tau_c$.
+Numerical artifacts introduced by this nonlinear fitting could also be responsible for the increased error seen with MESI at flow speeds between 3.5 to 6 mm/s.
+It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located.
 Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

### 2022-08-04 article.tex
Updated Adam's bio
Add Pawan to authors. Add bios for Chris and Pawan.

@@
 \author[a]{Adam Santorelli}
+\author[a]{Lisa M. Richards}
+\author[a]{Pawan K. Mannava}
 \author[a]{Christopher Smith}
-\author[a]{Lisa M. Richards}
 \author[a,*]{Andrew K. Dunn}
@@
 \subsection*{Author Contributions}
-C.T.S.
-and L.M.R.
+C.T.S., L.M.R., and P.K.M.
 constructed the imaging system, conceived the experiments, and acquired the data.
-C.T.S., A.S., and L.M.R.
-analyzed the results and wrote the manuscript.
+C.T.S., A.S., L.M.R., P.K.M., and C.S.
+analyzed the results.
+C.T.S, A.S., and L.M.R.
+wrote the manuscript.
 A.K.D.
@@
 
-\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin. He received his B.Eng., M.S.E., and Ph.D. in Electrical Engineering from McGill University.
+\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin.
+He received his B.Eng., M.S.E., and Ph.D.
+in Electrical Engineering from McGill University.
+He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway from 2017 to 2019.
+His current research is focused on the translational aspects of speckle imaging.
 
@@
 in Biomedical Engineering from the University of Texas at Austin.
+
+\vspace{2ex}\noindent\textbf{Pawan K.
+Mannava} was an undergraduate researcher at the University of Texas at Austin when this research was conducted.
+He received his B.S.
+in Biomedical Engineering from the University of Texas at Austin.
+
+\vspace{2ex}\noindent\textbf{Christopher Smith} is a graduate student at the University of Texas at Austin. He received his B.S. in Biomedical Engineering from the University of Houston.
 

### 2022-08-04 article.tex
Add supplement
Using text verbatim from Lisa draft

@@
 % ---------------------------------------------------------------------------------------
-
 \title{Using pressure-driven flow systems to evaluate laser speckle contrast imaging}
@@
 The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.).
-The outlet tubing drained into a vial, with the tubing end fully submerged in liquid.
+The outlet tubing drained into a vial, with the tubing end fully submerged in liquid (see Supplementary Material S1).
 A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.
@@
 This indicates that the stability results shown are typical and representative of actual performance differences.
-The $u_\textnormal{repeat}$ for the syringe pump across all flow steps (up to 1.86\%) was within the manufacturer's tolerances, which stated that instantaneous flow should be $\pm$2\% from the mean value.
+The $u_\textnormal{repeat}$ for the syringe pump across all flow steps (up to 1.86\%) was within the manufacturer's tolerances, which state that instantaneous flow should be $\pm$2\% from the mean value.
 The $u_\textnormal{repeat}$ for the pressure-regulated flow system (up to 0.55\%) slightly exceeded the manufacturer's specifications, which indicated that the best stability achievable with this system configuration was $\pm$0.5\% from the mean value.
@@
 Corresponding specifications were not available for the pressure-regulated flow system.
-While it is possible that using a glass syringe \cite{Zhou:2011ey} or sending the device for manufacturer recalibration could improve performance on the syringe pump, it is unlikely to achieve the stability and reliability seen with the pressure-regulated flow system.
+While it is possible that using a glass syringe \cite{Zhou:2011ey} or sending the device for manufacturer recalibration could improve performance on the syringe pump, it is unlikely to ever achieve the stability and reliability seen with the pressure-regulated flow system.
 

### 2022-08-04 supplement.tex
Add supplement
Using text verbatim from Lisa draft

\documentclass{article}

\usepackage[letterpaper]{geometry}
\usepackage{authblk}
\usepackage{graphicx}

% Prepend "S" on numbered items
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thefigure}{S\arabic{figure}}

% ---------------------------------------------------------------------------------------
% BEGIN TITLE AND AUTHORS
% ---------------------------------------------------------------------------------------
\title{Supplementary Material}

\author[a]{Colin T. Sullender}
\author[a]{Adam Santorelli}
\author[a]{Lisa M. Richards}
\author[a]{Pawan K. Mannava}
\author[a]{Christopher Smith}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, The University of Texas at Austin, Austin, TX, 78712, USA}

\date{}

% ----------------------------------------------------------------------------------------
% BEGIN DOCUMENT
% ----------------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Importance of submerging the microfluidic outlet line}

One important experimental detail that all previous plots took into account was recording the flow profiles while the outlet tubing from the phantom was submerged in solution, as shown in Figs. 2 and 3. This was performed after visualizing the dramatic decrease in flow observed when the outlet line was elevated and the solution dripped into the outlet vial. The release of the drop from the end of the tubing caused a large decrease in pressure, resulting in a flow decrease. This was observed with both flow control systems as shown in Fig.~\ref{fig:supplement_outlet}, meaning that it is an important experimental consideration for any microfluidic setup. These trials included approximately five-minute duration with the outlet line elevated and allowed to drip into the outlet vial, followed by submersion of the outlet line in the solution for another five minutes. Thus, the large spike in relative flow corresponds to the time point where the outlet line was manually submerged in solution.

% Figure S1 - Outlet Line Submersion
\begin{figure}
    \includegraphics[width=\textwidth]{FigureS1.png}
    \caption {
        Impact of submerging the outlet tubing after the phantom, shown for both flow control systems at 2.4 mm/s and 4.8 mm/s. These trials show approximately five-minute duration of the outlet tubing dripping into the outlet vial (seen by rapid flow drops), followed by five-minute duration of the outlet tubing submerged in solution. The baseline was set to either 2.4 mm/s (left) or 4.8 mm/s (right), using the average $\tau_{c}$ from each respective approximately five-minute duration flow profile after submerging the outlet tubing. The horizontal and vertical axes are the same across all plots. The 3 mL, 4.8 mm/s plot shows a zoomed view of the final drop in the dashed box, where the duration is 11.6 seconds.
    }
    \label{fig:supplement_outlet}
\end{figure}

Some general trends were observed from these trials. First, the magnitude of the flow decrease was larger for the syringe pump versus the pressure system. Because the pressure system has a higher compliance than the syringe pump, high frequency perturbations are dampened more by the pressure system. The frequency of the droplets was also very regular within trials. This suggests that the drop must reach a similar critical volume regardless of flow rate to overcome the surface tension required to release the drop from the tubing. The mean volume of the droplets can be estimated using the absolute flow rate from the flow sensor and the time between drops, and a standard deviation of <0.5 µL in drop volume was observed within each trial. The magnitude of the flow decrease was also larger for the slower flow (2.4 mm/s) versus the faster flow (4.8 mm/s) for all trials. This is likely due to the larger pressure differential generated at slower flows, since the pressure driving the flow is smaller for the slower speed. For the pressure system, the drops led to a 1.4 mbar change in pressure for the 2.4 mm/s speed (28.3 mbar average), and a 1.1 mbar change in pressure for the 4.8 mm/s speed (47.4 mbar average). A larger pressure change for a lower average pressure produces to a larger change in flow, which agrees with the larger magnitude flow drop seen for the slower speeds. Overall, these plots demonstrate that the user should be aware of the position of the outlet line during microfluidic data acquisition, and that submersion of the outlet line is critical to eliminate rapid flow changes caused by dripping from the outlet line.

% ----------------------------------------------------------------------------------------
% END
% ----------------------------------------------------------------------------------------
\end{document}

### 2022-08-05 supplement.tex
Update to customized Figure S1
Update figure caption

@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{FigureS1.png}
+    \includegraphics[width=\textwidth]{FigureS1.pdf}
     \caption {
-        Impact of submerging the outlet tubing after the phantom, shown for both flow control systems at 2.4 mm/s and 4.8 mm/s.
-These trials show approximately five-minute duration of the outlet tubing dripping into the outlet vial (seen by rapid flow drops), followed by five-minute duration of the outlet tubing submerged in solution.
-The baseline was set to either 2.4 mm/s (left) or 4.8 mm/s (right), using the average $\tau_{c}$ from each respective approximately five-minute duration flow profile after submerging the outlet tubing.
-The horizontal and vertical axes are the same across all plots.
-The 3 mL, 4.8 mm/s plot shows a zoomed view of the final drop in the dashed box, where the duration is 11.6 seconds.
+        Impact of submerging the microfluidic device outlet tubing for both flow control systems at 2.4 and 4.8 mm/s as measured with the inline flow sensor (blue) and single-exposure LSCI (red).
+These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the rapid periodic flow drops, followed by approximately five minutes of operation with the outlet tubing submerged in solution.
+All measurements were normalized to the average flow during the submerged segment of each experiment and compared to the ideal flow (black).
     }

### 2022-08-09 supplement.tex
Update supplement.tex

@@
 
-\usepackage[letterpaper]{geometry}
+\usepackage[letterpaper,margin=1in]{geometry}
 \usepackage{authblk}
@@
 
-One important experimental detail that all previous plots took into account was recording the flow profiles while the outlet tubing from the phantom was submerged in solution, as shown in Figs.
+An important methodological detail taken into account during all experiments was the submersion of the microfluidic outlet tubing in solution as depicted in the system schematics in Figs.
 2 and 3.
-This was performed after visualizing the dramatic decrease in flow observed when the outlet line was elevated and the solution dripped into the outlet vial.
-The release of the drop from the end of the tubing caused a large decrease in pressure, resulting in a flow decrease.
-This was observed with both flow control systems as shown in Fig.~\ref{fig:supplement_outlet}, meaning that it is an important experimental consideration for any microfluidic setup.
-These trials included approximately five-minute duration with the outlet line elevated and allowed to drip into the outlet vial, followed by submersion of the outlet line in the solution for another five minutes.
-Thus, the large spike in relative flow corresponds to the time point where the outlet line was manually submerged in solution.
+This strategy was adopted after visualizing dramatic changes in flow caused by the effluent dripping into the collection vial when the outlet line was elevated above the solution.
+The release of drops from the end of the tubing causes a large decrease in pressure, resulting in a flow decrease.
+This was observed with both flow control systems as shown in Fig.~\ref{fig:supplement_outlet}, indicating that this is an important experimental consideration for any microfluidic setup.
+These trials spanned ten minutes, with approximately five minutes of the effluent dripping into the collection vial before manually submerging the outlet line in the collected solution.
 
@@
         Impact of submerging the microfluidic device outlet tubing for both flow control systems at 2.4 and 4.8 mm/s as measured with the inline flow sensor (blue) and single-exposure LSCI (red).
-These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the rapid periodic flow drops, followed by approximately five minutes of operation with the outlet tubing submerged in solution.
-All measurements were normalized to the average flow during the submerged segment of each experiment and compared to the ideal flow (black).
+These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the periodic flow decreases, followed by five minutes of operation with the outlet tubing submerged in the collected solution.
+The large spike in relative flow around $t = $ 300 seconds corresponds to the outlet line being manually submerged in solution.
+All measurements were normalized to the average flow during the submerged segment of each trial and compared to the ideal flow (black).
     }
@@
 
-Some general trends were observed from these trials.
-First, the magnitude of the flow decrease was larger for the syringe pump versus the pressure system.
-Because the pressure system has a higher compliance than the syringe pump, high frequency perturbations are dampened more by the pressure system.
-The frequency of the droplets was also very regular within trials.
-This suggests that the drop must reach a similar critical volume regardless of flow rate to overcome the surface tension required to release the drop from the tubing.
-The mean volume of the droplets can be estimated using the absolute flow rate from the flow sensor and the time between drops, and a standard deviation of <0.5 µL in drop volume was observed within each trial.
-The magnitude of the flow decrease was also larger for the slower flow (2.4 mm/s) versus the faster flow (4.8 mm/s) for all trials.
-This is likely due to the larger pressure differential generated at slower flows, since the pressure driving the flow is smaller for the slower speed.
-For the pressure system, the drops led to a 1.4 mbar change in pressure for the 2.4 mm/s speed (28.3 mbar average), and a 1.1 mbar change in pressure for the 4.8 mm/s speed (47.4 mbar average).
-A larger pressure change for a lower average pressure produces to a larger change in flow, which agrees with the larger magnitude flow drop seen for the slower speeds.
-Overall, these plots demonstrate that the user should be aware of the position of the outlet line during microfluidic data acquisition, and that submersion of the outlet line is critical to eliminate rapid flow changes caused by dripping from the outlet line.
+Some general trends were observed across these trials.
+First, the magnitude of the flow decrease was larger for the syringe pump compared to the pressure-regulated flow system.
+Because the pressure-regulated system has a higher compliance than the syringe pump, high frequency perturbations are dampened more by the pressure-regulated system.
+Second, the frequency of the droplets was very regular within individual trials.
+This suggests that drops must reach a critical volume to overcome the surface tension in order to release from the tubing.
+Using the absolute flow rate from the inline sensor and the time between drops to estimate the mean volume, a standard deviation of \textless0.5 $\mu$L in drop volume was observed within each trial.
+Finally, the magnitude of the flow decrease was larger for the slower flow (2.4 mm/s) than the faster flow (4.8 mm/s) across all trials.
+This was likely caused by the larger pressure differential generated at slower flows, since the pressure driving the flow was lower for the slower flow rate.
+For example, with the pressure-regulated system, the drops led to a 1.4 mbar change at the 2.4 mm/s speed (28.3 mbar average) and a 1.1 mbar change at the 4.8 mm/s speed (47.4 mbar average).
+The larger relative pressure differential (4.95\% vs.
+2.3\%) produced a larger change in flow, which corresponds to the higher magnitude flow decreases seen at the slower flow rate.
+Overall, these results demonstrate that users should be aware of the positioning of the microfluidic outlet line during experiments and that submersion of the outlet tubing is critical to eliminate periodic flow perturbations caused by dripping.
 

### 2022-08-10 article.tex
Further revisions

@@
 Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}.
-Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution.
+Requiring only a laser for illumination and a camera for detection, LSCI can create full-field maps of motion with high spatiotemporal resolution.
 This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}.
@@
 Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output.
-A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments.
+A survey of over twenty LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments.
 The devices were from a variety of manufacturers and featured various syringe sizes and materials.
@@
 The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel.
-The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}.
+The square cross-section (1:1 aspect ratio) approximates the circular cross-section of vascular geometries \textit{in vivo}.
 The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring.
@@
 Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
-Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing.
-The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.).
+Tygon® microbore tubing (0.02$''$ inner diameter, Cole-Parmer Instrument Company, LLC) was connected to the blunt tip ports as inlet and outlet tubing.
+The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC).
 The outlet tubing drained into a vial, with the tubing end fully submerged in liquid (see Supplementary Material S1).
@@
 
-The syringe pump system (74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}.
+The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}.
 The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate.
@@
 While MESI exhibited slightly more variability during individual flow profile steps (Fig.
-\ref{fig:flow_mesi_lsci}a), this was likely caused by the fitting process required to calculate $\tau_c$.
+\ref{fig:flow_mesi_lsci}), this was likely caused by the fitting process required to calculate $\tau_c$.
 Numerical artifacts introduced by this nonlinear fitting could also be responsible for the increased error seen with MESI at flow speeds between 3.5 to 6 mm/s.
@@
 Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than systematic error.
-Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.
+Overall, these results indicate that highly accurate flow control is necessary for the reliable characterization of a MESI or LSCI system.
 
@@
 in Electrical Engineering from McGill University.
-He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway from 2017 to 2019.
+He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway.
 His current research is focused on the translational aspects of speckle imaging.

### 2022-08-10 supplement.tex
Further revisions

@@
 These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the periodic flow decreases, followed by five minutes of operation with the outlet tubing submerged in the collected solution.
-The large spike in relative flow around $t = $ 300 seconds corresponds to the outlet line being manually submerged in solution.
-All measurements were normalized to the average flow during the submerged segment of each trial and compared to the ideal flow (black).
+The large spike in relative flow around $t = $ 300 seconds corresponds to the outlet line being manually submerged in the solution.
+All measurements were normalized to the average flow during the submerged segment of each trial and compared to the ideal constant flow (black).
     }

### 2022-09-12 cover_letter.tex
Add cover letter

% Letter template based on StackExchange
% Werner: https://tex.stackexchange.com/a/583808
% Accessed 2022-09-12

\documentclass{article}

\usepackage[margin=1.25in]{geometry}
\usepackage{fancyhdr,graphicx}

\fancypagestyle{firstpage}{
    \fancyhf{} % Clear header/footer
    \renewcommand{\headrulewidth}{0pt}%
    \renewcommand{\footrulewidth}{0pt}%
}

\AtBeginDocument{\thispagestyle{firstpage}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex}

\begin{document}

\hfill
\begin{tabular}{ l @{} }
    Colin Sullender\\
    The University of Texas at Austin\\
    Department of Biomedical Engineering\\
    107 W. Dean Keeton Street Stop C0800\\
    Austin, TX, 78712, USA
\end{tabular}

\bigskip\bigskip

\begin{tabular}{ @{} l }
    \today \\[12pt] % Date
\end{tabular}

\bigskip

Dear Dr. Pogue,

\bigskip

We wish to submit a new manuscript entitled ''Using pressure-driven flow systems to evaluate laser speckle contrast imaging'' for consideration by \emph{Journal of Biomedical Optics}. We confirm that this work is original and has not been published elsewhere nor is it currently under consideration in another journal.

In this paper, we report on the characterization of laser speckle contrast imaging (LSCI) systems when using microfluidic flow phantoms. We evaluated the flow generation performance of a widely-used syringe pump controller compared to a pressure-regulated flow control system. The pressure-regulated system greatly outperformed the syringe pump across a range of flow speeds both in terms of stability and accuracy. The pressure-regulated flow system was then used to assess the performance of both single-exposure LSCI and multi-exposure speckle imaging (MESI) during stepped flow profile experiments. Consistent with prior work, MESI outperformed single-exposure LSCI at all tested flow speeds and more closely mirrored the programmed flow.

This work is significant because it demonstrates the importance of selecting a reliable flow control system when conducting microfluidic characterization studies. The use of syringe pumps introduces additional uncertainty to the resulting measurements that could mask the true sensitivity of an LSCI instrument. Our results suggest that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of flow measurement techniques. While we only evaluated LSCI/MESI, these findings are likely relevant for the broader dynamic light scattering community.

Please address all correspondence to Dr. Andrew Dunn at \underline{adunn@utexas.edu}.

Thank you for your consideration.

\bigskip

Sincerely,

\vspace{50pt}

Colin Sullender

\end{document}

### 2022-09-12 article.tex
Add grant numbers and update Andy's bio
Update disclosures

@@
 \subsection*{Disclosures}
-A.K.D. holds equity in and serves on the board of directors of Dynamic Light, Inc. The authors declare no other conflicts of interest.
+The authors declare no conflicts of interest.
 
@@
 \subsection*{Acknowledgments}
-This study was supported by the National Institutes of Health (Nos. ?)
+This study was supported by the National Institutes of Health (Nos. NS108484 and EB011556) and the UT Austin Portugal Program.
 
@@
 Hyman Endowed Chair in Engineering in the Department of Biomedical Engineering and the Director of the Center for Emerging Imaging Technologies (CEIT) at the University of Texas at Austin.
-He pioneered the use of laser speckle contrast imaging to measure blood flow in the brain and has more than 50 publications on the subject.
+He pioneered the use of laser speckle contrast imaging to measure blood flow in the brain.
 His research focuses on the development of novel optical imaging techniques for studying the brain.

### 2022-09-12 cover_letter.tex
Update cover_letter.tex

@@
 
-This work is significant because it demonstrates the importance of selecting a reliable flow control system when conducting microfluidic characterization studies.
+This work is significant because it demonstrates the importance of selecting a reliable flow control system when characterizing optical techniques such as laser speckle imaging or laser Doppler.
 The use of syringe pumps introduces additional uncertainty to the resulting measurements that could mask the true sensitivity of an LSCI instrument.

### 2022-09-16 article.tex
Strip author bios and figure/table list for bioRxiv submission

@@
 % ----------------------------------------------------------------------------------------
-% AUTHOR BIOGRAPHIES
-% ----------------------------------------------------------------------------------------
-\vspace{1ex}
-\vspace{2ex}\noindent\textbf{Colin T.
-Sullender} is a postdoctoral fellow at the University of Texas at Austin.
-He received his B.S.
-in Bioengineering from the University of Washington and his M.S.E and Ph.D.
-in Biomedical Engineering from the University of Texas at Austin.
-His current research focuses on developing laser speckle contrast imaging techniques for studying neurovascular hemodynamics.
-
-\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin.
-He received his B.Eng., M.S.E., and Ph.D.
-in Electrical Engineering from McGill University.
-He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway.
-His current research is focused on the translational aspects of speckle imaging.
-
-\vspace{2ex}\noindent\textbf{Lisa M.
-Richards} was a postdoctoral fellow at the University of Texas at Austin when this research was conducted.
-She received her B.S.E in Biomedical Engineering from Duke University and her M.S.E.
-and Ph.D.
-in Biomedical Engineering from the University of Texas at Austin.
-
-\vspace{2ex}\noindent\textbf{Pawan K.
-Mannava} was an undergraduate researcher at the University of Texas at Austin when this research was conducted.
-He received his B.S.
-in Biomedical Engineering from the University of Texas at Austin.
-
-\vspace{2ex}\noindent\textbf{Christopher Smith} is a graduate student at the University of Texas at Austin. He received his B.S. in Biomedical Engineering from the University of Houston.
-
-\vspace{2ex}\noindent\textbf{Andrew K.
-Dunn} is the Edward S.
-Hyman Endowed Chair in Engineering in the Department of Biomedical Engineering and the Director of the Center for Emerging Imaging Technologies (CEIT) at the University of Texas at Austin.
-He pioneered the use of laser speckle contrast imaging to measure blood flow in the brain.
-His research focuses on the development of novel optical imaging techniques for studying the brain.
-
-% ----------------------------------------------------------------------------------------
-% FIGURE AND TABLE LISTS
-% ----------------------------------------------------------------------------------------
-\listoffigures
-\listoftables
-
-% ----------------------------------------------------------------------------------------
 % END

### 2022-12-12 article.tex
Add T32 to funding
Initial draft of reviewer response

--- 2022-09-12 article.tex
@@
 For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}.
-This speed can be converted to a volumetric flow rate using the cross-sectional area of the flow channel, which is then used to program the flow control system.
+This speed can be converted to a volumetric flow rate using the cross-sectional area of the flow channel, which can then be used to program the flow controller.
 
-Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output.
+Syringe pumps are the most widely used flow control system in microfluidic studies and are generally believed to provide a highly-controlled flow output.
 A survey of over twenty LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments.
@@
 
-Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Zhou:2011ey,Li:2014ca,Zeng.2020}.
+Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Bong.2010,Zhou:2011ey,Li:2014ca,Zeng.2020}.
 These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate \cite{Zeng.2020}.
@@
 The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties at near infrared wavelengths ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}.
-The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom.
+The PDMS-\ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom.
 Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.
@@
 The square cross-section (1:1 aspect ratio) approximates the circular cross-section of vascular geometries \textit{in vivo}.
-The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring.
+The PDMS-\ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring.
 The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold.
-The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel.
+The microchannel side of the phantom was then oxygen plasma bonded to a glass slide to seal the channel.
 Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal.
@@
 The outlet tubing drained into a vial, with the tubing end fully submerged in liquid (see Supplementary Material S1).
-A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.
+A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the \ce{TiO2}-doped PDMS with the glass slide sealing the surface.
 
@@
 To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel.
-A thermal mass flow sensor (FLU-L, 0.03 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a.
-The sensor output was digitized and relayed to a computer via an accompanying hub (Flowboard, FLB, Fluigent, Inc.) where the MAESFLO software (Fluigent, Inc.) was used to monitor and record the absolute flow rate.
+A thermal mass flow sensor (FLU-L, 0 $\pm$ 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a.
+This flow rate range corresponds to flow speeds of 0 $\pm$ 77.8 mm/s in the microfluidic channel.
+The sensor output was relayed to a computer via an accompanying hub (Flowboard, FLB, Fluigent, Inc.) where the MAESFLO software (Fluigent, Inc.) was used to monitor and record the absolute flow rate.
 All flow sensor measurements were downsampled from 10 Hz to 2 Hz using interpolation to match the timing of the optical measurements.
@@
 
-Two stepped flow profile experiments were conducted to assess each flow system using the commercial flow sensor.
+Two separate stepped flow profile experiments were conducted to assess each flow system using the commercial flow sensor.
 First, a 3-step flow profile was used to determine the uncertainty of each flow control system.
@@
 For these measurements, it was assumed that $\beta=1$, which exclusively allows for the computation of relative flow changes.
-The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).
+The resulting timecourse of $\tau_c$ values was resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).
 
@@
 Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm.
-The camera exposures were temporally synchronized with the modulated laser pulses.
+The camera exposures were temporally synchronized with the modulated laser pulses from the AOM.
 Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of approximately 2.5 fps.
@@
 The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments.
-Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile.
+Each speed was maintained for two minutes with a total experiment duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile.
 MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps).
@@
 All fitting was performed with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in MATLAB (R2021a, MathWorks, Inc.).
-The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation, smoothed temporally with a central moving average filter ($k=5$), and inverted to obtain $ICT$.
+The resulting timecourse of $\tau_c$ values was resampled to 2 Hz using interpolation, smoothed temporally with a central moving average filter ($k=5$), and inverted to obtain $ICT$.
 
@@
 Furthermore, the close agreement between LSCI and the flow sensor demonstrates that these anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations.
+Such a conclusion would underestimate the true performance of an LSCI or MESI system being evaluated for real-world applications.
 Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials.
@@
 It also remains to be seen whether calibrations performed in controlled microfluidic environments can reliably be translated to animal or human subjects since \textit{in vivo} measurements sample a range of different vessels \cite{Davis:2016ik,Jafari.2020}.
+However, if microfluidics are necessary for the calibration process, these results demonstrate that a pressure-regulated flow system should be used in order to produce stable, repeatable, and accurate flow.
 
@@
 \subsection*{Acknowledgments}
-This study was supported by the National Institutes of Health (Nos. NS108484 and EB011556) and the UT Austin Portugal Program.
+The authors would like to acknowledge Jason R.
+Cook for machining the aluminum mold used to cast the microfluidic channel.
+The authors would also like to thank Sertan Kutal Gökçe for providing the oxygen plasma bonding procedure, which was used to fabricate the microfluidic phantom.
+This study was supported by the National Institutes of Health (Nos.
+NS108484, EB011556, and EB007507) and the UT Austin Portugal Program.
 
